---
title: "Aim 1 Quant Survey - PPW"
author: "David Owaga & Yuwei Wang"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, echo = F, include = F}
rm(list = ls())

pacman::p_load(knitr, tidyverse, ggplot2, psych, janitor, dplyr, 
               openxlsx, gtsummary, kableExtra, ggrepel, UpSetR,
               funModeling, gt, gtExtras,likert, summarytools, 
               ggstats) 

knitr::opts_chunk$set(fig.width = 12, fig.height = 10)

# read data
data <- read.csv("C:/Users/DAMARIS/Desktop/IPMH/Quantitative Survey/IPMHAim1Quantitative_DATA_2024-10-02_0823.csv")

# Quick overview of the selected columns
data %>% 
    dplyr::select(redcap_event_name, women_pregnancy, women_gestational, women_delivery, women_preg_before, women_preg_number, women_education, women_partner, women_employment) %>% 
    dfSummary(
        graph.col = TRUE,
        style = "grid",
        graph.magnif = 0.75
    ) %>% 
    stview()
```

## Women Demographics

Altogether, we currently have data for  `r sum(data$redcap_event_name == "survey_arm_1")` participants.

```{r Basic Demographic Summary, echo=F, message=FALSE, warning=FALSE}
ppw_data <- data %>% 
    filter(redcap_event_name == "survey_arm_1")

ppw_demo <- ppw_data %>%
  dplyr::select(record_id, cal_age, starts_with("women_"), demographics_perinatal_women_complete, pmad_phq1, pmad_phq2, 
         pmad_gad1, pmad_gad2) %>%
  filter(!is.na(women_participant_id)) %>% 
    mutate(age = as.numeric(case_when(women_dob_uk == 1 ~ floor(cal_age),
                         women_dob_uk == 0 ~ women_age))) %>% 
  mutate(women_pregnancy = dplyr::recode(women_pregnancy,
                                         "1" = "Pregnant",
                                         "0" = "Postpartum")) %>% 
    mutate(phq2_scores = pmad_phq1 + pmad_phq2,
           gad2_scores = pmad_gad1 + pmad_gad2,
           pmad = ifelse(phq2_scores >= 3 | gad2_scores >= 3, 1, 0))

ppw_demo <- ppw_demo %>% 
  mutate(women_education = dplyr::recode(women_education, 
                                       "1" = "No formal education",
                                       "2" = "Primary - not completed",
                                       "3" = "Primary completed", 
                                       "4" = "Secondary - not completed", 
                                       "5" = "Secondary - completed",
                                       "6" = "Above secondary / tertiary"),
         women_education = fct_relevel(women_education,
                                       "Above secondary / tertiary", "Primary completed", "Secondary - not completed", "Secondary - completed", "Primary - not completed", "No formal education")) %>%
  mutate(women_service = dplyr::case_when(
      women_service___1 == "1" ~ "First Antenatal care visit",
      women_service___2 == "1" ~ "Follow-up antenatal care visit",
      women_service___3 == "1" ~  "Postnatal care",
      women_service___4 == "1"~ "Immunization for my baby",
      women_service___5 == "1" ~ "PMTCT",
      women_service___6 == "1"~ "Family planning",
      women_service___7 == "1" ~ "Other",)) %>%
    mutate(women_facility = dplyr::recode(women_facility, 
                                    "0" = "Specialist",
                                   "1" = "Rwambwa Sub-county Hospital",
                                   "2" = "Sigomere Sub County Hospital",
                                   "3" = "Uyawi Sub County Hospital",
                                   "4" = "Got Agulu Sub-District Hospital",
                                   "5" = "Ukwala Sub County Hospital",
                                   "6" = "Madiany Sub County Hospital",
                                   "7" = "Kabondo Sub County Hospital",
                                   "8" = "Mbita Sub-County Hospital",
                                   "11" = "Nyandiwa Level IV Hospital",
                                   "13" = "Ober Kamoth Sub County Hospital",
                                   "14" = "Gita Sub County Hospital",
                                   "15" = "Akala Health Centre",
                                   "16" = "Usigu Health Centre",
                                   "17" = "Ramula Health Centre",
                                   "18" = "Simenya Health Centre",
                                   "19" = "Airport Health Centre (Kisumu)",
                                   "20" = "Nyalenda Health Centre",
                                   "21" = "Mirogi Health Centre",
                                   "22" = "Ndiru Level 4 Hospital"),
           women_partner = dplyr::recode(women_partner,
                                         "1" = 	"No partner, single",
                                         "2" = "Unsteady boyfriend (on and off)",
                                         "3" = "Steady boyfriend",
                                         "4" = "Married, monogamous",
                                         "5" = "Married, polygamous",
                                         "6" = "Divorced/widowed",
                                         "7" = "Separated",
                                         "8" = "Prefer not to answer"),
            women_partner = fct_relevel(women_partner,
                                      "Married, monogamous", "No partner, single", "Married, polygamous", "Divorced/widowed", "Steady boyfriend")) %>% 
  mutate(women_gestational = as.numeric(women_gestational)) %>% 
  mutate(women_delivery = as.numeric(women_delivery)) %>% 
    mutate(women_employment = dplyr::recode(women_employment,
                                            "1" = "Unemployed",
                                            "2" = "Salaried",
                                            "3" = "On wages (Irregular salary, kibarua)",
                                            "4" = "Self-employed",
                                            "5" = "Student",
                                            "6" = "Out of work and looking for work",
                                            "7" = "Out of work but not currently looking for work",
                                            "8" = "A homemaker",
                                            "9" = "Other"),
           women_employment = case_when(
               women_employment == "Other" ~ women_employment_other,
               TRUE ~ women_employment),
           women_employment = fct_relevel(women_employment,
                                          "Salaried", "Self-employed", "Unemployed", "Student", "On wages (Irregular salary, kibarua)", "A homemaker", "Out of work and looking for work","Out of work but not currently looking for work" )) %>% 
    mutate(women_residence = dplyr::recode(women_residence,
                                           "1" = "Urban or city center",
                                           "2" = "Peri-urban areas",
                                           "3" = "Rural areas or countryside"),
           women_residence = fct_relevel(women_residence,
                                         "Rural areas or countryside", "Peri-urban areas", "Urban or city center"),
           women_distance = dplyr::recode(women_distance,
                                          "0" = "< an hour",
                                          "1" = ">= an hour")) %>% 
    mutate(women_hiv = dplyr::recode(women_hiv,
                                     "1"  = "HIV negative",
                                     "2" = "Living with HIV",
                                     "99" = "Don't know",
                                     "-2" =	"Prefer not to answer")) %>% 
    mutate(women_art = dplyr::recode(women_art,
                                     "1" = "Yes",
                                     "0" = "No",
                                     "-2" = "I prefer not to say"))

# basic demo table
ppw_demo %>% tbl_summary(
  include=c(age, women_service___4, women_service___2, women_service___1,
            women_service___3, women_pregnancy, women_gestational,
            women_delivery, women_preg_number, women_education, women_partner,
            women_employment,women_residence, women_distance, women_distance_0, 
            women_distance_1, women_hiv, women_hiv_history, women_art, pmad),
  label = list(age ~ "Age (Years)",
               women_education ~ "Education level",
               women_gestational ~ "Gestational age (weeks)",
               women_service___1 ~ "First Antenatal care visit",
               women_service___2 ~ "Follow-up antenatal care visit",
               women_service___3 ~ "Postnatal care",
               women_service___4 ~ "Immunization for my baby",
               women_pregnancy ~ "Pregnancy Status",
               women_delivery ~ "Weeks since delivery",
               women_preg_number ~ "Total number of pregnancies",
               women_partner ~ "Kind of partner",
               women_employment ~ "Employment status",
               women_residence ~ "Residential area",
               women_distance ~ "Duration to the facility",
               women_distance_0 ~ "Duration to the facility (Munites)",
               women_distance_1 ~ "Duration to the facility (Hours)",
               women_hiv ~ "HIV status",
               women_art ~ "Currently using antiretroviral therapy",
               women_hiv_history ~ "Duration known LHIV (years)",
               pmad ~ "PHQ2 or QAD2 => 3"),
  missing = "no",
  digits = list(all_continuous() ~ 1), 
  type = list(age ~ "continuous", 
              women_gestational ~ "continuous",
              women_delivery ~ "continuous",
              women_preg_number ~ "continuous",
              women_distance_0 ~ "continuous",
              women_distance_1 ~ "continuous",
              women_hiv_history ~ "continuous"),
  statistic = list(all_continuous() ~ "{median} [IQR: {p25}, {p75}]")) %>% 
  bold_labels() %>%
    add_n() %>% 
    italicize_levels() %>%
  # convert from gtsummary object to gt object
  as_gt() %>%
  # modify with gt functions
  gt::tab_header("Table 1: Basic Demographic Summary for Women") %>% 
  gt::tab_options(
    table.font.size = "medium",
    data_row.padding = gt::px(1)) 

```


## SCREENING
```{r PMAD Screening Summary, echo=FALSE, message=FALSE, warning=FALSE}
screen_ppw <- ppw_data  %>%
  dplyr::select(record_id, starts_with("scr_diff_"), screening_access, screening_strategy_other, screening_complete, screening_times, starts_with("scr_barrier"))
```



### Impact of Screening Strategies
```{r Screening Strategies, echo=F, message=FALSE, warning=FALSE}
screening_strategies <- screen_ppw %>% 
    dplyr::select(starts_with("scr_diff_"))


# Define the mapping
likert_mapping <- c(
    "Major negative impact",
    "Some negative impact",
    "No impact",
    "Some positive impact ",
    "Major positive impact")


# Apply the mapping
screening_strategies <- screening_strategies %>%
  mutate(across(everything(), ~ likert_mapping[.])) 

# Trim white spaces
screening_strategies <- screening_strategies %>%
  mutate_all(trimws)

# Set factor levels
levels <- c(
    "Major negative impact",
    "Some negative impact",
    "No impact",
    "Some positive impact ",
    "Major positive impact")


screening_strategies <- screening_strategies %>%
  lapply(function(x) factor(x, levels = levels)) %>%
  as.data.frame()


gglikert(
  screening_strategies,
  variable_labels = c(
      scr_diff_service = "Integrating screening as part of routine care in the clinic",
      scr_diff_trainexist = "Training existing providers on how to handle patients with mental illnesses",
      scr_diff_room = "Having a dedicated private place for MH screening" ,
      scr_diff_provide = "Having providers whose work is dedicated to offering mental health support",
      scr_diff_special = "Having providers and counsellors with specialized mental health training",
      scr_diff_aware = "Creating awareness on mental health in the community for example using community health promoters or through churches",
      scr_diff_confi =  "Assuring confidentiality in mental health services",
      scr_diff_stigma = "Not talking to providers I already know about mental health issues",
      scr_diff_atti = "[Having friendly and respectful providers" 
  ),
  sort = "descending",
         sort_prop_include_center = TRUE,
         labels_accuracy = 1,
         labels_hide_below = 0.05)+
    labs(title = "Impact of Screening Strategies",
         caption = "Note: n = 190") +  # Add a footnote
    theme(plot.caption = element_text(hjust = 0.5),
          plot.title = element_text(hjust = 0.5))+  # Center the footnote
  scale_fill_brewer(palette = "RdYlBu")

```


### Criticality of  Screening Barriers
```{r Screening Barriers, echo=F, message=FALSE, warning=FALSE}
screening_barries <- screen_ppw %>% 
    dplyr::select(starts_with("scr_barrier_"))


# Define the mapping
likert_mapping <- c(
    "Not a challenge at all",
    "Makes it a little hard",
    "Makes it hard",
    "Makes it very hard",
    "Makes it impossible")


# Apply the mapping
screening_barries <- screening_barries %>%
  mutate(across(everything(), ~ likert_mapping[.])) 

# Trim white spaces
screening_barries <- screening_barries %>%
  mutate_all(trimws)

# Set factor levels
levels <- c(
    "Not a challenge at all",
    "Makes it a little hard",
    "Makes it hard",
    "Makes it very hard",
    "Makes it impossible")


screening_barries <- screening_barries %>%
  lapply(function(x) factor(x, levels = levels)) %>%
  as.data.frame()


gglikert(
  screening_barries,
  variable_labels = c(
      scr_barrier_room = "Not having a private space to talk about mental health in the facilities",
      scr_barrier_norm = "Having signs of depression and anxiety as normal to you thus you do not see a need to seek care",
      scr_barrier_provide = "Not having a specific provider to talk about mental health issues in the facilities" ,
      scr_barrier_special = "Lack of providers with specialized MH training",
      scr_barrier_confi = "Fear of breach of confidentiality by providers",
      scr_barrier_workload = "Provider not having time to ask about depression or anxiety as they are attending to many women",
      scr_barrier_partner =  "Lack of male partner involvement and support",
      scr_barrier_witch = "Women believing mental illness is as a result of witchcraft, hence they don't talk about it",
      scr_barrier_stigmacom = "Fear of being judged by family members and community members",
      scr_barrier_stigmahcw = "Fear of being judged by providers",
      scr_barrier_aware = "Lack of awareness or knowledge on mental illnesses",
      scr_barrier_avail = "Screening for MH not being available and you not being asked by the healthcare provider about your MH during the visits",
      scr_barrier_atti = "Providers being inapproachable"),
  sort = "descending",
         sort_prop_include_center = TRUE,
         labels_accuracy = 1,
         labels_hide_below = 0.05)+
    labs(title = "Criticality of Screening Barriers",
         caption = "Note: n = 190") +  # Add a footnote
    theme(plot.caption = element_text(hjust = 0.5),
          plot.title = element_text(hjust = 0.5))+  # Center the footnote
  scale_fill_brewer(palette = "RdYlBu")

```


# Diagnosis and Treatment
```{r Diagnosis and Treatment, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dia_treat_ppw <- ppw_data %>% 
  dplyr::select(record_id, starts_with("dx_"), starts_with("trt_"), starts_with("dxt_"), diagnosis_and_treatment_complete) %>% 
    mutate(dx_access = dplyr::recode(dx_access,
                                     "1" = "Yes - both depression and anxiety",
                                     "2" = "Yes - only depression",
                                     "3" = "Yes - only anxiety",
                                     "0" = "No"),
           dx_access = fct_relevel(dx_access, "No", "Yes - only depression",
                                   "Yes - only anxiety", "Yes - both depression and anxiety"),
           dx_depression = dplyr::recode(dx_depression,
                                         "0" = "During the pregnancy",
                                         "1" = "After delivery"),
           dx_depression = fct_relevel(dx_depression,
                                       "During the pregnancy", "After delivery"),
           dx_anxiety = dplyr::recode(dx_anxiety,
                                      "0" = "During the pregnancy",
                                      "1" = "After delivery"),
           trt_times = dplyr::recode(trt_times,
                                     "1" = "Less than 2 times",
                                     "2" = "Less than 2 times"))

dia_treat_ppw <- dia_treat_ppw %>%
  mutate(trt_type_counseling = case_when(
    grepl("general counselling", trt_type_counseling, TRUE ~ trt_type_counseling) ~ "General Counselling",
    grepl("Interpersonal counselling.|Interpersonal counselling", trt_type_counseling, ignore.case = TRUE) ~ "Interpersonal Counselling",
    grepl("supportive counselling", trt_type_counseling, ignore.case = TRUE) ~ "Supportive Counselling",
    grepl("unspecified counselling|Unspecified counselling|unspecified counselling", trt_type_counseling, ignore.case = TRUE) ~ "Unspecified Counselling",
    trt_type_counseling == "" | is.na(trt_type_counseling) ~ NA_character_,  # Set to NA if empty or NA
    TRUE ~ trt_type_counseling  # Keep original value if no match
  ))%>% 
    mutate(trt_type_counseling = fct_relevel(trt_type_counseling,
                                             "Unspecified Counselling", "Interpersonal Counselling", "General Counselling", "Supportive Counselling"))


dia_treat_ppw %>% 
    tbl_summary(
        include = c(dx_access, dx_depression, dx_depression_before,
                    dx_depression_after, dx_anxiety, dx_anxiety_before,
                    trt_caretype___1, trt_type_counseling,
                    trt_times),
        label = list(dx_access ~ "Ever been diagnosed with depression and/or anxiety",
               dx_depression ~ "Diagnosed depression during or after pregnancy",
               trt_caretype___1 ~ "Counselling",
               dx_anxiety ~ "Diagnosed anxiety during or after pregnancy",
               dx_anxiety_before ~ "Gestational age (month) diagnosed with anxiety",
               trt_times ~ "Times treated of depression and/or anxiety in last 2 months",
               trt_type_counseling ~ "Type of counselling",
               dx_depression_before ~ "Gestational age (month) diagnosed with depression",
               dx_depression_after ~ "Diagnosed with depression after delivery in Month"),
    digits = list(all_continuous() ~ 1), 
  type = list(dx_depression_before ~ "continuous",
              dx_depression_after ~ "continuous",
              dx_anxiety_before ~ "continuous"),
        missing = "no") %>% 
    bold_labels() %>%
    add_n() %>% 
    italicize_levels() %>% 
  # convert from gtsummary object to gt object
  as_gt() %>%
  # modify with gt functions
  gt::tab_header("Table 2: Diagnosis and Treatment Summary for PPW") %>% 
  gt::tab_options(
    table.font.size = "medium",
    data_row.padding = gt::px(1)) 

trt_times <- ppw_data %>% 
    dplyr::select(record_id, dx_access, trt_times) %>% 
    filter(!is.na(trt_times))

```



### Criticality of Diagnosis and Treatment Barriers 
```{r criticality of barriers to Diagnosis and Treatment, echo=FALSE, message=FALSE, warning=FALSE}
criticality_df <- dia_treat_ppw %>% 
    select(starts_with("dxt_barrier_"))%>%
  mutate(across(where(is.numeric), ~ na_if(., 99))) %>% 
     select(-dxt_barrier_other)


# Define the mapping
likert_mapping <- c(
    "Not a challenge at all",
    "Makes it a little hard",
    "Makes it hard",
    "Makes it very hard",
    "Makes it impossible")


# Apply the mapping
criticality_df <- criticality_df %>%
  mutate(across(everything(), ~ likert_mapping[.]))

# Trim white spaces
criticality_df <- criticality_df %>%
  mutate_all(trimws)

# Set factor levels
levels <- c(
    "Not a challenge at all",
    "Makes it a little hard",
    "Makes it hard",
    "Makes it very hard",
    "Makes it impossible")


criticality_df <- criticality_df %>%
  lapply(function(x) factor(x, levels = levels)) %>%
  as.data.frame()


gglikert(
  criticality_df,
  variable_labels = c(
      dxt_barrier_service = "Not being asked about mental health during the visits",
      dxt_barrier_atti = "Providers being inapproachable",
      dxt_barrier_stigmahcw = "Fear of being judged by providers" ,
      dxt_barrier_stigmacom = "Fear of being judged by family members and community members",
      dxt_barrier_room = "Not having a private space for mental health treatment in the facilities",
      dxt_barrier_where = "Not knowing where to seek help for depression or anxiety",
      dxt_barrier_provide =  "Not having a specific provider to talk about mental health issues in the facilities",
      dxt_barrier_special = "Lack of providers with specialized MH training",
      dxt_barrier_transport = "Transport to get care is difficult",
      dxt_barrier_confi = "Fear of breach of confidentiality by providers", 
      dxt_barrier_fear = "Fear of not getting the mental health support or treatment needed",
      dxt_barrier_priority = "Having conflicting priorities such as work",
      dxt_barrier_norm = "Having signs of depression and anxiety is normal to you thus you do not see a need to seek care",
      dxt_barrier_finan = "Getting care is expensive",
      dxt_barrier_workload = "Provider not having time to provide depression or anxiety treatment or not keeping appointments as scheduled",
     dxt_barrier_religion = "Prefer going for traditional medicine or prayers instead of speaking with a provider",
     dxt_barrier_witch = "Women believing that mental illness is as a result of witchcraft and as such they don't go for treatment",
     dxt_barrier_partner = "Lack of male partner involvement and support",
     dxt_barrier_drug = "Lack of drugs in the facility"  
  ),
  sort = "descending",
         sort_prop_include_center = TRUE,
         labels_accuracy = 1,
         labels_hide_below = 0.05)+
    labs(title = "Criticality of Diagnosis and Treatment Barriers",
         caption = "Note: n = 190") +  # Add a footnote
    theme(plot.caption = element_text(hjust = 0.5),
          plot.title = element_text(hjust = 0.5))+  # Center the footnote
  scale_fill_brewer(palette = "RdYlBu")
```


### Impact of Diagnosis and Treatment Strategies
```{r Impact of strategies, echo=FALSE, message=FALSE, warning=FALSE}
impact_df <- dia_treat_ppw %>% 
    select(starts_with("dxt_diff_"))%>%
  mutate(across(where(is.numeric), ~ na_if(., 99)))

# Define the mapping
likert_mapping <- c('Never', 'Rarely', 'Occasionaly', 'Frequently', 'Alyways')

# Apply the mapping
impact_df <- impact_df %>%
  mutate(across(everything(), ~ likert_mapping[.]))

# Trim white spaces
impact_df <- impact_df %>%
  mutate_all(trimws)

# Set factor levels
levels <- c('Never', 'Rarely', 'Occasionaly', 'Frequently', 'Alyways')

impact_df <- impact_df %>%
  lapply(function(x) factor(x, levels = levels)) %>%
  as.data.frame()

gglikert(impact_df,
         variable_labels = c(
             dxt_diff_service ="Integrating MH treatment routine care",
             dxt_diff_trainexist = "MH training to existing providers",
             dxt_diff_room = "Private room for HM treatment", 
             dxt_diff_provide = "Having mental health providers",
             dxt_diff_transport = "Transport facilitation",
             dxt_diff_aware = "MH community awareness",
             dxt_diff_chv = "Using CHVs to support MH",
             dxt_diff_special = "Having MH specialized providers"),
         sort = "descending",
         sort_prop_include_center = TRUE,
         labels_accuracy = 1,
         labels_hide_below = 0.05,
         width = 0.5)+
    labs(title = "Impact of Diagnosis and Treatment Strategies",
         caption = "Note: n = 190") +  # Add a footnote
    theme(plot.caption = element_text(hjust = 0.5),
          plot.title = element_text(hjust = 0.5),)  # Center the footnote

```


## Referral And Remission
```{r Rerem, echo=F, warning=F, message=F}
rerem_ppw <- ppw_data %>% 
    dplyr::select(record_id, refer_access, refer_facility___1, 
                  refer_facility___2, refer_facility___3, 
                  refer_facility___4, refer_facility___5, 
                  refer_facility_other, rem_access, starts_with("rerem_"),
                  referral_and_remission_complete)


#Referral Summary
ppw_data %>% 
    tbl_summary(
  include=c(refer_access, refer_facility___1, refer_facility___2, refer_facility___3, refer_facility___4, refer_facility___5, rem_access),
  label = list(refer_access ~ "Refered to receive care for PMAD",
               refer_facility___1 ~ "Jaramogi Oginga Odinga TRH",
               refer_facility___2 ~ "Homa Bay TRH",
               refer_facility___3 ~ "Siaya TRH",
               refer_facility___4 ~	"Kisumu CRH",
               refer_facility___5 ~	"Other",
               rem_access ~ "Received treatment multiple times with the provider monitoring symptoms"),
  missing = "no",
  digits = list(all_continuous() ~ 1),
  statistic = list(all_continuous() ~ "{median} [IQR: {p25}, {p75}]")) %>% 
  bold_labels() %>%
    add_n() %>% 
    italicize_levels() %>% 
  # convert from gtsummary object to gt object
  as_gt() %>%
  # modify with gt functions
  gt::tab_header("Table 1: Referral and Remission Summary for PPW") %>% 
  gt::tab_options(
    table.font.size = "medium",
    data_row.padding = gt::px(1)) 
    

```



## Frequency of Barriers
```{r Frequency of Barriers, echo = F, warning = F, message = F}
freq_bar_ppw <- ppw_data %>% 
    dplyr::select(record_id, starts_with("freq_barr_"), frequency_of_barriers_complete) %>%
  mutate(across(where(is.numeric), ~ na_if(., 99)))

freq_bar_df <- freq_bar_ppw %>% 
    dplyr::select(2:21)%>% 
  dplyr::rename("Not being asked during the visits" = freq_barr_service,
          "Inapproachable providers" = freq_barr_atti,
          "Lack of private room" = freq_barr_room,
         "Having signs isnormal" = freq_barr_norm,
         "Lack of specilaist communication in facility" = freq_barr_provide,
         "Lack of specialized MH providers" = freq_barr_special,
         "Confidentiality by providers" = freq_barr_confi,
         "Providers lack of time to provide MH services)" = freq_barr_workload,
         "Lack of male partner involvement" = freq_barr_partner,
         "Believing it is witchcraft" = freq_barr_witch,
          "Fear family members and community judgement " = freq_barr_stigmacom,
          "Fear of being judged by providers" = freq_barr_stigmahcw,
         "Lack of awareness or knowledge" = freq_barr_aware,
         "Not knowing where to seek help" = freq_barr_where,
         "Transport to get care is difficult" = freq_barr_transport,
        "Fear of not getting treatment needed" = freq_barr_fear,
        "Having conflicting priorities" = freq_barr_priority,
        "Getting care is expensive" = freq_barr_finan,
        "Prefer traditional medicine or prayers " = freq_barr_religion,
        "Lack of drugs in the facility" = freq_barr_drug)

# Define the mapping
likert_mapping <- c('Never', 'Rarely', 'Occasionaly', 'Frequently', 'Alyways')

# Apply the mapping
freq_bar_df <- freq_bar_df %>%
  mutate(across(everything(), ~ likert_mapping[.]))

# Trim white spaces
freq_bar_df <- freq_bar_df %>%
  mutate_all(trimws)

# Set factor levels
levels <- c('Never', 'Rarely', 'Occasionaly', 'Frequently', 'Alyways')

freq_bar_df <- freq_bar_df %>%
  lapply(function(x) factor(x, levels = levels)) %>%
  as.data.frame()


results <- likert(freq_bar_df)

plot <- plot(results, text.size = 5, centered = FALSE)+
    theme_bw(base_size = 10)+
    theme(legend.position = "right")+
    labs(title = "How frequently have you experienced these Barriers to receiving MH services since your most recent pregnancy?",
         caption = "Note: n = 190") +  # Add a footnote
    theme(plot.caption = element_text(hjust = 0.5),
          plot.title = element_text(hjust = 0.5),)  # Center the footnote
    
plot
```


## IPMH

```{r Criticality of IPMH barriers to Screning, echo=F, message=FALSE, warning=FALSE}
ipmh_ppw <- ppw_data %>% 
    dplyr::select(record_id, starts_with("ip_scre_"), 
                  starts_with("freq_scre_"),
                  starts_with("ip_"),
                  	ipmh_complete)

ipmh_screening_barriers <- ipmh_ppw %>% 
    select(starts_with("ip_scre_barr_"))

# Define the mapping
likert_mapping <- c('Not a challenge at all', 'Makes it a little hard', 'Makes it hard', 'Makes it very hard', 'Makes it impossible')

# Apply the mapping
ipmh_screening_barriers <- ipmh_screening_barriers %>%
  mutate(across(everything(), ~ likert_mapping[.]))

# Trim white spaces
ipmh_screening_barriers <- ipmh_screening_barriers %>%
  mutate_all(trimws)

# Set factor levels
levels <- c('Not a challenge at all', 'Makes it a little hard', 'Makes it hard', 'Makes it very hard', 'Makes it impossible')

ipmh_screening_barriers <- ipmh_screening_barriers %>%
  lapply(function(x) factor(x, levels = levels)) %>%
  as.data.frame()


gglikert(ipmh_screening_barriers,
         variable_labels = c(
             ip_scre_barr_workload ="Increased provider workload therefore screening using PHQ9/GAD7 may not be done well",
             ip_scre_barr_confi = "Fear of breach of confidentiality by providers",
             ip_scre_barr_familiar = "Familiarity with the provider may prevent women from accepting the intervention"),
         sort = "descending",
         sort_prop_include_center = TRUE,
         labels_accuracy = 1,
         labels_hide_below = 0.05,
         width = 0.5)+
    labs(title = "Criticality of IPMH Barriers to Screening",
         caption = "Note: n = 190") +  # Add a footnote
    theme(plot.caption = element_text(hjust = 0.5),
          plot.title = element_text(hjust = 0.5),)  # Center the footnote

```


```{r Frequency of IPMH barriers to Screning, echo=F, message=FALSE, warning=FALSE}
screen_barriers_fre <- ipmh_ppw %>% 
    select(starts_with("freq_scre_"))

# Define the mapping
likert_mapping <- c('Never', 'Rarely(once)', 'Occasionally', 'Frequently', 'Always')

# Apply the mapping
screen_barriers_fre <- screen_barriers_fre %>%
  mutate(across(everything(), ~ likert_mapping[.]))

# Trim white spaces
screen_barriers_fre <- screen_barriers_fre %>%
  mutate_all(trimws)

# Set factor levels
levels <- c('Never', 'Rarely(once)', 'Occasionally', 'Frequently', 'Always')

screen_barriers_fre <- screen_barriers_fre %>%
  lapply(function(x) factor(x, levels = levels)) %>%
  as.data.frame()


gglikert(screen_barriers_fre,
         variable_labels = c(
             freq_scre_workload ="Increased provider workload therefore screening using PHQ9/GAD7 may not be done well",
             freq_scre_confi = "Fear of breach of confidentiality by providers",
             freq_scre_familiar = "Familiarity with the provider may prevent women from accepting the intervention"),
         sort = "descending",
         sort_prop_include_center = TRUE,
         labels_accuracy = 1,
         labels_hide_below = 0.05,
         width = 0.5)+
    labs(title = "Frequency of IPMH Barriers to Screening",
         caption = "Note: n = 190") +  # Add a footnote
    theme(plot.caption = element_text(hjust = 0.5),
          plot.title = element_text(hjust = 0.5),)  # Center the footnote


```


```{r Impact of IPMH Strategies to Screning, echo=F, message=FALSE, warning=FALSE}
ipmh_strategies <- ipmh_ppw %>% 
    select(starts_with("ip_scre_diff_"))

# Define the mapping
likert_mapping <- c('Major negative impact', 'Some negative impact', 'No impact', 'Some positive impact', 'Major positive impact')

# Apply the mapping
ipmh_strategies <- ipmh_strategies %>%
  mutate(across(everything(), ~ likert_mapping[.]))

# Trim white spaces
ipmh_strategies <- ipmh_strategies %>%
  mutate_all(trimws)

# Set factor levels
levels <- c('Major negative impact', 'Some negative impact', 'No impact', 'Some positive impact', 'Major positive impact')

ipmh_strategies <- ipmh_strategies %>%
  lapply(function(x) factor(x, levels = levels)) %>%
  as.data.frame()


gglikert(ipmh_strategies,
         variable_labels = c(
             ip_scre_diff_entrance ="Providing IPMH screening at the entrance of the facility or at the triage area",
             ip_scre_diff_familiar = "Recruiting new healthcare workers with whom clients have no familiarity with",
             ip_scre_diff_atti = "Having friendly and respectful providers",
             ip_scre_diff_provide = "Have providers whose work is dedicated to offering MH support"),
         sort = "descending",
         sort_prop_include_center = TRUE,
         labels_accuracy = 1,
         labels_hide_below = 0.05,
         width = 0.5)+
    labs(title = "Impact of IPMH Strategies to Screening",
         caption = "Note: n = 190") +  # Add a footnote
    theme(plot.caption = element_text(hjust = 0.5),
          plot.title = element_text(hjust = 0.5),)  # Center the footnote

```


#### Criticality of IPMH Barriers to PM+
```{r Criticality of IPMH Barriers to PM+, echo=FALSE, message=FALSE, warning=FALSE}
ip_pm_barr <- ppw_data %>% 
    select(starts_with("ip_trt_barr_"))

# Define the mapping
likert_mapping <- c('Not a challenge at al', 'Makes it a little hard', 'Makes it hard', 'Makes it very hard', 'Makes it impossible')

# Apply the mapping
ip_pm_barr <- ip_pm_barr %>%
  mutate(across(everything(), ~ likert_mapping[.]))

# Trim white spaces
ip_pm_barr <- ip_pm_barr %>%
  mutate_all(trimws)

# Set factor levels
levels <- c('Not a challenge at al', 'Makes it a little hard', 'Makes it hard', 'Makes it very hard', 'Makes it impossible')

ip_pm_barr <- ip_pm_barr %>%
  lapply(function(x) factor(x, levels = levels)) %>%
  as.data.frame()


gglikert(ip_pm_barr,
         variable_labels = c(
             ip_trt_barr_transport ="Transporting to attend sessions is difficult",
             ip_trt_barr_many = "Having many sessions",
             ip_trt_barr_atti = "Providers being inapproachable"),
         sort = "descending",
         sort_prop_include_center = TRUE,
         labels_accuracy = 1,
         labels_hide_below = 0.05,
         width = 0.5)+
    labs(title = "Criticality of IPMH Barriers to PM+",
         caption = "Note: n = 190") +  # Add a footnote
    theme(plot.caption = element_text(hjust = 0.5),
          plot.title = element_text(hjust = 0.5),)  # Center the footnote

```



#### Frequency of IPMH Barriers Accessing PM+ Services
```{r Frequency of IPMH Barriers Accessing PM+ Services, echo=FALSE, message=FALSE, warning=FALSE}
ip_pm_barr_freq <- ppw_data %>% 
    dplyr::select(freq_trt_transport, freq_trt_many, 
                  freq_trt_atti)


# Define the mapping
likert_mapping <- c('Never', 'Rarely', 'Occasionally', 'Frequently', 'Always')

# Apply the mapping
ip_pm_barr_freq <- ip_pm_barr_freq %>%
  mutate(across(everything(), ~ likert_mapping[.]))

# Trim white spaces
ip_pm_barr_freq <- ip_pm_barr_freq %>%
  mutate_all(trimws)

# Set factor levels
levels <- c('Never', 'Rarely', 'Occasionally', 'Frequently', 'Always')

ip_pm_barr_freq <- ip_pm_barr_freq %>%
  lapply(function(x) factor(x, levels = levels)) %>%
  as.data.frame()


gglikert(ip_pm_barr_freq,
         variable_labels = 
             c(
             freq_trt_transport = "Transporting to attend sessions is difficult",
             freq_trt_many = "Having many sessions",
             freq_trt_atti = "Providers being inapproachable"),
         sort = "descending",
         sort_prop_include_center = TRUE,
         labels_accuracy = 1,
         labels_hide_below = 0.05,
         width = 0.5)+
    labs(title = "Frequency of IPMH Barriers to Accessing PM+ Services",
         caption = "Note: n = 190") +  # Add a footnote
    theme(plot.caption = element_text(hjust = 0.5),
          plot.title = element_text(hjust = 0.5),)  # Center the footnote
```


#### Impact of IPMH Strategies on Accessing PM+ Services
```{r Impact of IPMH Strategies on Accessing PM+ Services, echo=FALSE, message=FALSE, warning=FALSE}
ip_pm_strategies <- ppw_data %>% 
    dplyr::select(starts_with("ip_trt_diff_"))


# Define the mapping
likert_mapping <- c('Major negative impact', 'Some negative impact', 'No impact', 'Some positive impact', 'Major positive impact')

# Apply the mapping
ip_pm_strategies <- ip_pm_strategies %>%
  mutate(across(everything(), ~ likert_mapping[.]))

# Trim white spaces
ip_pm_strategies <- ip_pm_strategies %>%
  mutate_all(trimws)

# Set factor levels
levels <- c('Major negative impact', 'Some negative impact', 'No impact', 'Some positive impact', 'Major positive impact')

ip_pm_strategies <- ip_pm_strategies %>%
  lapply(function(x) factor(x, levels = levels)) %>%
  as.data.frame()


gglikert(ip_pm_strategies,
         variable_labels = 
             c(
             ip_trt_diff_atti = "Having friendly and respectful providers",
             ip_trt_diff_train = "Training healthcare providers",
             ip_trt_diff_hcw = "Recruiting new healthcare workers with whom clients have no familiarity with",
             ip_trt_diff_provide = "Having providers whose work is dedicated to offering MH support"),
         sort = "descending",
         sort_prop_include_center = TRUE,
         labels_accuracy = 1,
         labels_hide_below = 0.05,
         width = 0.5)+
    labs(title = "Impact of Strategies on Accessing PM+ Services",
         caption = "Note: n = 190") +  # Add a footnote
    theme(plot.caption = element_text(hjust = 0.5),
          plot.title = element_text(hjust = 0.5),)  # Center the footnote
```


### Telepsychiatry
#### Criticality of IPMH barriers to Telepsychiatry
```{r Criticality of IPMH Telepsychiatry barriers, echo=FALSE, message=FALSE, warning=FALSE}
criticality_barr <-ppw_data  %>%
    dplyr::select(starts_with("ip_tele_barr_"))


# Define the mapping
likert_mapping <- c('Not a challenge at all', 'Makes it a little hard', 'Makes it hard', 'Makes it very hard', 'Makes it impossible')


# Apply the mapping
criticality_barr <- criticality_barr %>%
  mutate(across(everything(), ~ likert_mapping[.])) 

# Trim white spaces
criticality_barr <- criticality_barr %>%
  mutate_all(trimws)

# Set factor levels
levels <- c('Not a challenge at all', 'Makes it a little hard', 'Makes it hard', 'Makes it very hard', 'Makes it impossible')


criticality_barr <- criticality_barr %>%
  lapply(function(x) factor(x, levels = levels)) %>%
  as.data.frame()


gglikert(
  criticality_barr,
  variable_labels = c(
      ip_tele_barr_internet = "Internet connectivity for telepsychiatry",
      ip_tele_barr_drug = "Difficult to get mental health medication",
      ip_tele_barr_prefer = "Not comfortable with video format for MH appointments",
      ip_tele_barr_tech = "Challenge in using technology as women may experience technical di culties with doing the videocall",
      ip_tele_barr_examine = "Difficulty showing the physical problem (the
 cause of the MH issue",
      ip_tele_barr_finan = "The drugs recommended may be expensive"),
  sort = "descending",
         sort_prop_include_center = TRUE,
         labels_accuracy = 1,
         labels_hide_below = 0.05)+
    labs(title = "Criticality of IPMH barriers to Telepsychiatry",
         caption = "Note: n = 190") +  # Add a footnote
    theme(plot.caption = element_text(hjust = 0.5),
          plot.title = element_text(hjust = 0.5))+  # Center the footnote
  scale_fill_brewer(palette = "RdYlBu",  
                    guide = guide_legend(title = "Likert Scale"))
```


#### Frequency of IPHM Barriers to Accessing Telepsychiatry Services
```{r Frequency of IPMH barriers to Telepsychiatry,  echo=FALSE, message=FALSE, warning=FALSE}
tele_barr_df <-ppw_data  %>%
    dplyr::select(starts_with("freq_tele_"))


# Define the mapping
likert_mapping <- c('Never', 'Rarely', 'Occasionaly', 'Frequently', 'Always')


# Apply the mapping
tele_barr_df <- tele_barr_df %>%
  mutate(across(everything(), ~ likert_mapping[.])) 

# Trim white spaces
tele_barr_df <- tele_barr_df %>%
  mutate_all(trimws)

# Set factor levels
levels <- c('Never', 'Rarely', 'Occasionaly', 'Frequently', 'Alyways')


tele_barr_df <- tele_barr_df %>%
  lapply(function(x) factor(x, levels = levels)) %>%
  as.data.frame()


gglikert(
  tele_barr_df,
  variable_labels = c(
      freq_tele_internet = "Internet connectivity for telepsychiatry",
      freq_tele_drug = "Difficult to get mental health medication",
      freq_tele_finan = "The drugs recommended may be expensive",
      freq_tele_prefer = "Not comfortable with video format for MH appointments",
      freq_tele_tech = "Technology Hurdles for Women in Video Calls",
      freq_tele_examine = "Challenges in Demonstrating Physical Issues in Tele"),
  sort = "descending",
         sort_prop_include_center = TRUE,
         labels_accuracy = 1,
         labels_hide_below = 0.05)+
    labs(title = "Frequency of IPMH Barriers to receiving Telepsychiatry",
         caption = "Note: n = 190") +  # Add a footnote
    theme(plot.caption = element_text(hjust = 0.5),
          plot.title = element_text(hjust = 0.5))+  # Center the footnote
  scale_fill_brewer(palette = "RdYlBu",  
                    guide = guide_legend(title = "Likert Scale"))
```



#### Impact of IPMH Strategies on Telepsychiatry
```{r Impact of IPMH Strategies on Telepsychiaty, echo=FALSE, message=FALSE, warning=FALSE}
tele_stratergies <- ppw_data %>% 
    dplyr::select(starts_with("ip_tele_diff_"))


# Define the mapping
likert_mapping <- c('Major negative impact', 'Some negative impact', ' No impact', 'Some positive impact', ' Major positive impact')


# Apply the mapping
tele_stratergies <- tele_stratergies %>%
  mutate(across(everything(), ~ likert_mapping[.])) 

# Trim white spaces
tele_stratergies <- tele_stratergies %>%
  mutate_all(trimws)

# Set factor levels
levels <- c('Major negative impact', 'Some negative impact', ' No impact', 'Some positive impact', ' Major positive impact')


tele_stratergies <- tele_stratergies %>%
  lapply(function(x) factor(x, levels = levels)) %>%
  as.data.frame()


gglikert(
  tele_stratergies,
  variable_labels = c(
      ip_tele_diff_inperson = "Bringing the psychiatrist in-person regularly",
      ip_tele_diff_internet = "Install strong internet connectivity",
      ip_tele_diff_wifi = "Government to provide free WIFI"),
  sort = "descending",
         sort_prop_include_center = TRUE,
         labels_accuracy = 1,
         labels_hide_below = 0.05)+
    labs(title = "Impact of IPMH Strategies on Telepsychiatry",
         caption = "Note: n = 190") +  # Add a footnote
    theme(plot.caption = element_text(hjust = 0.5),
          plot.title = element_text(hjust = 0.5))+  # Center the footnote
  scale_fill_brewer(palette = "RdYlBu",  
                    guide = guide_legend(title = "Likert Scale"))

```



```{r GAD2 & PHQ2 Results, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
phq_gad2_scores <- ppw_demo %>% 
    select(record_id, pmad_gad1, pmad_gad2, pmad_phq1, pmad_phq2)

```

```{r PPW age in months, include=FALSE}
age_months <- ppw_data %>% 
    select(record_id,  collect_time, women_dob_uk, women_dob, women_age, cal_age) %>%
    mutate(age = as.numeric(case_when(
        women_dob_uk == 1 ~ round(cal_age*12),
        women_dob_uk == 0 ~ round(women_age * 12)))) %>% 
    mutate(interview_age = format(as.Date(collect_time), "%m/%d/%Y"))%>% 
    select(record_id, age, interview_age) 

# Perform left join by 'record_id' to generate dataframe for NDA report
nda_df <- age_months %>%
  left_join(phq_gad2_scores, by = "record_id")


    
```

