---
title: "IPMH_Audit_Feedback"
author: "Yuwei Wang"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, echo = F, include = F, warning=F}
rm(list = ls())

source("Audit and feedback script.R")
```

This script generates the audit and feedback report for each facility based on the calendar months. For the first audit and feedback session, we will report statistics from the beginning of the study till March 15th. Data from the report should be abstracted for each facility and put into the slide template.

# 1. PHQ2 and GAD2 Screening Rate Per Facility (Per week & Per month & Total)

```{r, line plots for each facility, echo = F, warning=F, fig.width = 6, fig.height = 4}
facilities <- unique(screening_rate_weekly$study_site)

for (facility in facilities) {
  facility_data <- screening_rate_weekly %>% filter(study_site == facility)
  
  p <- ggplot(facility_data, aes(x = week, y = screening_rate)) +
    geom_line(color = "blue") + 
    geom_point(color = "red") +
    labs(title = paste("Weekly PHQ2/GAD2 Screening Rate -", facility),
         x = "Week", 
         y = "PHQ2/GAD2 screening Rate (%)") +
    theme_minimal() +
    theme(axis.text.x = element_text(hjust = 1),
          plot.title = element_text(size = 12)) +
      scale_x_date(date_breaks = "1 week", date_labels = "%Y-%m-%d") +
      scale_y_continuous(limits = c(20, 120))
  
  print(p)  # This will generate separate plots for each facility
}
```

```{r, monthly screening rate table, echo = F, warning=F}
kable(screening_rate_monthly, 
      caption = "Monthly PHQ2/GAD2 Screening Rate by Facility",
      digits = 2)
```

```{r, total screening rate table per facility, echo = F, warning=F}
kable(total_screening_rate, 
      caption = "Total PHQ2/GAD2 Screening Rate by Facility",
      digits = 2)
```

\newpage

# 2. PHQ9 and GAD7 Screening Rate Among Study Participants Per Facility (Per week & Per month & Total)

```{r, phq9 line plots for all facilities, echo = F, warning=F, fig.width=6, fig.height=4}
facilities <- unique(phq9_screening$clt_study_site)

for (facility in facilities) {
  facility_data <- phq9_screening_weekly %>% filter(clt_study_site == facility)
  
  p <- ggplot(facility_data, aes(x = week, y = `PHQ9/GAD7 screening rate`)) +
    geom_line(color = "blue") + 
    geom_point(color = "red") +
    labs(title = paste("Weekly PHQ9/GAD7 Screening Rate -", facility),
         x = "Date", 
         y = "PHQ9/GAD7 Screening Rate (%)") +
    theme_minimal() +
    theme(axis.text.x = element_text(hjust = 1),
          plot.title = element_text(size = 12)) +
    scale_x_date(date_breaks = "1 week", date_labels = "%Y-%m-%d") +
    scale_y_continuous(limits = c(0, 100))
  
  print(p)  # This will generate separate plots for each facility
}
```

```{r, monthly secondary screening rate table, echo = F, warning=F}
kable(phq9_screening_monthly, 
      caption = "PHQ9/GAD7 Monthly Screening Rate by Facility",
      digits = 2)
```

```{r, total secondary screening rate table, echo = F, warning=F}
kable(phq9_screening_total, 
      caption = "Total PHQ9/GAD7 Screening Rate by Facility",
      digits = 2)
```

\newpage

# 3. PM+ Referral Rate Per Facility (Per month & Total)

```{r, pm referral rate, echo = F, warning=F}
kable(pm_referral_monthly, 
      caption = "Monthly PM+ Referral Rate by Facility",
      digits = 2)

kable(pm_referral_total,
      caption = "Total PM+ Referral Rate by Facility",
      digits = 2)
```

\newpage

# 4. Telepsychiatry Referral Rate Per Facility (Per month & Total)

```{r, telepsych referral rate, echo = F, warning=F}
kable(monthly_referral_summary_tele, caption = "Monthly Telepsychiatry Referral Rate by Facility",
      digits = 2)

kable(total_referral_summary_tele, caption = "Total Telepsychiatry Referral Rate by Facility",
      digits = 2)
```

\newpage

# 5. PM+ initiation rate per facility (Per month & Total)

```{r, pm initiation rate, echo = F, warning=F}
kable(pm_summary_session1%>% select(1,2,3,4,7), 
      caption = "Monthly PM+ Initiation Rate (Session 1) by Facility",
      digits = 2)

kable(pm_initiation_all_merge_session1,
      caption = "Total PM+ Initiation Rate by Facility",
      digits = 2)
```
\newpage

# 6. PM+ completion rate per facility (Per month & Total)

No data yet. No completion rate data available for the first audit and feedback session.

\newpage

# 7. Telepsychiatry initiation rate per facility (Per month & Total)

No initiation data yet. Kabondo Sub County Hospital has two referrals for telepsychiatry, but no initiation data is available for the first audit and feedback session.

\newpage

# 8. Frequency of conducting health talks & use of flipbook per facility (Per month & Total)

```{r health talks, echo = F, warning=F}
kable(health_talks, caption = "Monthly Health Talks & Flipbook Usage by Facility",
      digits = 2)
kable(total_health_talks, caption = "Total Health Talks & Flipbook Usage by Facility",
      digits = 2)
```
