---
title: "IPMH_Audit_Feedback"
author: "Yuwei Wang"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, echo = F, include = F, warning=F}
rm(list = ls())

knitr::opts_chunk$set(fig.width = 10, fig.height = 12)

#Read data using datapull
source("REDCap_datapull.R")

##### main database needed
#Data close out survey 
#PHQ2/GAD2 abstraction database
#PHQ9/GAD7 abstraction form in the PPW longitudinal database
#PM+ session survey
#Telepsychiatry session survey

#drop all other datasets
rm(list = ls()[! ls() %in% c("daily_closeout", "phq2_gad2_abstract", "rct_ppw", "pm", "telepsych", "rct_ppw_consenting")])

#Ensure date columns are in proper format
daily_closeout$rct_dcr_date <- as.Date(daily_closeout$rct_dcr_date)
phq2_gad2_abstract$screening_date <- as.Date(phq2_gad2_abstract$screening_date) 
rct_ppw$clt_timestamp <- as.Date(rct_ppw$clt_timestamp)
pm$pm_date <- as.Date(pm$pm_date)
telepsych$telepsych_date <- as.Date(telepsych$telepsych_date)

#uniform study site number for all datasets
phq2_gad2_abstract <- phq2_gad2_abstract %>%
  mutate(study_site = str_replace(study_site, "^\\d+,\\s*", ""))

rct_ppw <- rct_ppw %>%
  mutate(clt_study_site = str_replace(clt_study_site, "^\\d+,\\s*", ""))

rct_ppw <- rct_ppw %>% 
    filter(is.na(redcap_repeat_instrument))

head(daily_closeout)
head(phq2_gad2_abstract)
head(rct_ppw)
head(pm)
head(telepsych)

#manually making sure record_id in abstraction database do not have space
phq2_gad2_abstract$record_id <- str_replace(phq2_gad2_abstract$record_id, " ", "")
```

This script generates the audit and feedback report for each facility based on the calendar months. The report includes the following sections:

# 1. PHQ2 and GAD2 Screening Rate Per Facility (Per day & Per month)

```{r, first screening, echo = F, warning=F}
###### This is using the n_total of abstraction data##########
###### We should use this part of the code to cross-check data accuracy#####

# #Aggregate PHQ2/GAD2 screening rate per study site and day
# screening_rate <- phq2_gad2_abstract %>%
#   mutate(day = floor_date(screening_date, "day")) %>%
#   group_by(study_site, day) %>%
#   summarise(num_screened = n(), .groups = "drop")
# 
# # Aggregate total ANC clients from daily closeout data
# total_anc_clients <- daily_closeout %>%
#   mutate(day = floor_date(rct_dcr_date, "day")) %>%
#   group_by(rct_facility_name, day) %>%
#   summarise(total_anc_clients = sum(rct_anc_number, na.rm=T), .groups = "drop")
# 
# # Merge the two datasets
# screening_rate <- left_join(screening_rate, total_anc_clients, by = c("study_site" = "rct_facility_name", "day" = "day"))
# 
# #calculate screening rate
# screening_rate <- screening_rate %>%
#   mutate(screening_rate = num_screened / total_anc_clients * 100)
# 
# ggplot(screening_rate, aes(x = day, y = screening_rate, color = study_site)) +
#   geom_line() +
#   geom_point() +
#   labs(title = "Daily Screening Rate by Facility",
#        x = "Date",
#        y = "Screening Rate (%)") +
#   theme_minimal() +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))

##another way of checking###
#get the total number of clients screened per facility per day using abstraction dataset
num_screened <- phq2_gad2_abstract %>%
  group_by(study_site, screening_date) %>%
  summarise(num_screened = n(), .groups = "drop")

#compare this with rct_screening in daily closeout data
daily_closeout %>%
  mutate(day = floor_date(rct_dcr_date, "day")) %>%
  group_by(rct_facility_name, day) %>%
  summarise(rct_screening = sum(rct_screening, na.rm = TRUE), .groups = "drop") %>%
  left_join(num_screened, by = c("rct_facility_name" = "study_site", "day" = "screening_date")) %>%
  mutate(diff = rct_screening - num_screened) %>%
  filter(diff != 0) %>% knitr::kable()
#rct_screening is the number of clients screened in the daily closeout data
#num_screened is the number of clients screened in the abstraction data

##total number per facility [comparison]
daily_closeout %>%
  group_by(rct_facility_name) %>%
  summarise(total_anc_clients = sum(rct_anc_number, na.rm = TRUE), .groups = "drop")




############using daily closeout data only ################
#Aggregate PHQ2/GAD2 screening rate per study site and day
screening_rate_daily <- daily_closeout %>%
  mutate(day = floor_date(rct_dcr_date, "day")) %>%
  group_by(rct_facility_name, day) %>%
  summarise(screening_rate = rct_screening/rct_anc_number, .groups = "drop")

ggplot(screening_rate_daily, aes(x = day, y = screening_rate, 
                                 color = rct_facility_name)) +
  geom_line() +
  geom_point() +
  labs(title = "Daily Screening Rate by Facility",
       x = "Date", 
       y = "Screening Rate (%)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

```{r, line plots for all facilities, echo = F, warning=F}
facilities <- unique(screening_rate_daily$rct_facility_name)

for (facility in facilities) {
  facility_data <- screening_rate_daily %>% filter(rct_facility_name == facility)
  
  p <- ggplot(facility_data, aes(x = day, y = screening_rate)) +
    geom_line(color = "blue") + 
    geom_point(color = "red") +
    labs(title = paste("Daily Screening Rate -", facility),
         x = "Date", 
         y = "Screening Rate (%)") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
  print(p)  # This will generate separate plots for each facility
}
```

```{r, monthly screening rate table, echo = F, warning=F}
monthly_screening_summary <- daily_closeout %>%
  mutate(month = format(rct_dcr_date, "%Y-%m")) %>%
  group_by(rct_facility_name, month) %>%
  summarise(
    num_screened = sum(rct_screening, na.rm = TRUE),
    total_anc_clients = sum(rct_anc_number, na.rm = TRUE),
    screening_rate = (num_screened / total_anc_clients) * 100,
    .groups = "drop"
  )
kable(monthly_screening_summary, caption = "Monthly Screening Rate by Facility",
      digits = 2)
```

\newpage

# 2. PHQ9 and GAD7 Screening Rate Among Study Participants Per Facility (Per day and Per month)

```{r, second screening, echo = F, warning=F}

#denomintor should just be the number of participants




#first change the options to numeric
phq2_gad2_abstract <- phq2_gad2_abstract %>%
  mutate(across(c(abs_rct_phq2_1, abs_rct_phq2_2, abs_rct_gaq2_1, abs_rct_gaq2_2), 
                ~ case_when(
                  . == "Not at all (0 days)" ~ 0,
                  . == "Several days (1-7 days)" ~ 1,
                  . == "More than half of the days (8-11 days)" ~ 2,
                  . == "Nearly every day (12-14 days)" ~ 3,
                  TRUE ~ NA_real_
                ), 
                .names = "{.col}_number"))  
#calculate PHQ2/GAD2 score in the abstraction dataset
phq2_gad2_abstract <- phq2_gad2_abstract %>%
  mutate(score_phq2 = abs_rct_phq2_1_number + abs_rct_phq2_2_number,
         score_gad2 = abs_rct_gaq2_1_number + abs_rct_gaq2_2_number)

#merge the anc number in the consenting database into the rct_ppw dataset
enroll_anc_number <- rct_ppw_consenting %>%
  filter(!is.na(partipant_id)) %>%
  select(partipant_id, anc_num)

rct_ppw <- rct_ppw %>%
  left_join(enroll_anc_number, by = c("clt_ptid" = "partipant_id")) 

# filter those in phq2_gad2_abstract who can find a matching anc number in the rct_ppw dataset
phq2_gad2_abstract_enroll <- phq2_gad2_abstract %>%
  filter(record_id %in% rct_ppw$anc_num)
#technically n of this dataset should be the same as the n of rct_ppw, but it is way less (ANC number change might be one reason).

# Aggregate total women with PHQ2/GAD2 scores ??? 3 (Denominator)
phq2_high_scores <- phq2_gad2_abstract_enroll %>%
  filter(score_phq2 >= 3 | score_gad2 >= 3) %>%
  mutate(day = floor_date(screening_date, "day")) %>%
  group_by(study_site, day) %>%
  summarise(total_high_scores = n(),
            anc_number = record_id,
            .groups = "drop")

#######Here we can cross-check if this number is consistent with the rct_enrollment in the daily_closeout dataset########
daily_closeout %>%
  mutate(day = floor_date(rct_dcr_date, "day")) %>%
  group_by(rct_facility_name, day) %>%
  summarise(rct_enrollment = sum(rct_enrollment, na.rm = TRUE), .groups = "drop") %>%
  left_join(phq2_high_scores, by = c("rct_facility_name" = "study_site", "day" = "day")) %>%
  mutate(diff = rct_enrollment - total_high_scores) %>%
  filter(diff != 0) %>% knitr::kable()

# get the numerator from rct_ppw dataset [n participant got screened]
phq9_screening <- rct_ppw %>%
  filter(!is.na(rct_ppw$abs_phq_tired)) %>%
  mutate(day = floor_date(clt_timestamp, "day")) %>%
  group_by(clt_study_site, day) %>%
  summarise(num_screened = n(), 
            pt_id = clt_ptid,
            .groups = "drop")
nrow(phq9_screening) #42

# Merge the two datasets
phq9_screening <- left_join(phq9_screening, phq2_high_scores[, -4], 
                            by = c("clt_study_site" = "study_site", "day" = "day"))
####This does not make any sense - so much missing data in this merged dataset.
####Basically what this tells me is that we don't have all phq2/gad2 data

#calculate screening rate
phq9_screening <- phq9_screening %>%
  mutate(screening_rate = num_screened / total_high_scores * 100)

ggplot(phq9_screening, aes(x = day, y = screening_rate, 
                           color = clt_study_site)) +
  geom_line() +
  geom_point() +
  labs(title = "Daily Screening Rate by Facility",
       x = "Date", 
       y = "Screening Rate (%)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r, phq9 line plots for all facilities, echo = F, warning=F}
facilities <- unique(phq9_screening$clt_study_site)

for (facility in facilities) {
  facility_data <- phq9_screening %>% filter(clt_study_site == facility)
  
  p <- ggplot(facility_data, aes(x = day, y = screening_rate)) +
    geom_line(color = "blue") + 
    geom_point(color = "red") +
    labs(title = paste("Daily Screening Rate -", facility),
         x = "Date", 
         y = "Screening Rate (%)") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
  print(p)  # This will generate separate plots for each facility
}
```

```{r, monthly secondary screening rate table, echo = F, warning=F}
#make phq9_screening have one row per day per facility
phq9_screening <- phq9_screening %>%
  distinct(clt_study_site, day, .keep_all = TRUE)

monthly_screening_summary <- phq9_screening %>%
  mutate(month = format(day, "%Y-%m")) %>%
  group_by(clt_study_site, month) %>%
  summarise(
    num_screened = sum(num_screened, rm.na = TRUE),
    total_high_scores = sum(total_high_scores, rm.na = TRUE),
    screening_rate = (num_screened / total_high_scores) * 100,
    .groups = "drop"
  )
monthly_screening_summary
```

\newpage

# 3. PM+ Referral Rate Per Facility (Per month)

We don't have many participants who need referral for PM+ every day so we will calculate the referral rate per month only.

```{r, pm referral rate, echo = F, warning=F}
#first change the options to numeric
rct_ppw <- rct_ppw %>%
  mutate(across(c(starts_with("abs_phq")), 
                ~ case_when(
                  . == "not at all" ~ 0,
                  . == "several days" ~ 1,
                  . == "more than half the days" ~ 2,
                  . == "nearly every day" ~ 3,
                  TRUE ~ NA_real_
                ), 
                .names = "{.col}_number")) 
rct_ppw <- rct_ppw %>%
  mutate(across(c(starts_with("abs_gad")), 
                ~ case_when(
                  . == "Not at all" ~ 0,
                  . == "Several days" ~ 1,
                  . == "More than half the days" ~ 2,
                  . == "Nearly every day" ~ 3,
                  TRUE ~ NA_real_
                ), 
                .names = "{.col}_number")) 

#calculate PHQ9/GAD7 score
rct_ppw <- rct_ppw %>%
  mutate(
    score_phq9 = rowSums(across(starts_with("abs_phq") & ends_with("_number")), na.rm = TRUE),
    score_gad7 = rowSums(across(starts_with("abs_gad") & ends_with("_number")), na.rm = TRUE)
  )

# Aggregate total women with PHQ9/GAD7 scores ??? 10 and < 15 (Denominator)
phq9_high_scores <- rct_ppw %>%
  filter((score_phq9 >= 10 & score_phq9 <15 )| 
             (score_gad7 >= 10 & score_gad7 <15)) %>%
  mutate(day = floor_date(clt_timestamp, "day")) %>%
  group_by(clt_study_site, day) %>%
  summarise(total_high_scores = n(),
            .groups = "drop")

# get the numerator from rct_ppw database
pm_referral <- rct_ppw %>% 
    filter(abs_phq_ref_pm == "Yes" | abs_gad7_ref_pm == "Yes") 
### this might not work (people might check one but not the other)

pm_referral <- pm_referral %>%
  mutate(day = floor_date(clt_timestamp, "day")) %>%
  group_by(clt_study_site, day) %>%
  summarise(num_referred = n(), .groups = "drop")

# Merge the two datasets
pm_referral <- left_join(pm_referral, phq9_high_scores, 
                         by = c("clt_study_site" = "clt_study_site", "day" = "day"))
#there are missing data in the merged dataset. And it's impossible to have a total_high_scores bigger than num_referred.

#calculate referral rate
pm_referral <- pm_referral %>%
  mutate(referral_rate = num_referred / total_high_scores * 100)

# ggplot(pm_referral, aes(x = day, y = referral_rate, 
#                         color = clt_study_site)) +
#   geom_line() +
#   geom_point() +
#   labs(title = "Daily Referral Rate by Facility",
#        x = "Date", 
#        y = "Referral Rate (%)") +
#   theme_minimal() +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r, monthly pm referral rate table, echo = F, warning=F}
#make pm_referral have one row per day per facility
pm_referral <- pm_referral %>%
  distinct(clt_study_site, day, .keep_all = TRUE)

monthly_referral_summary <- pm_referral %>%
  mutate(month = format(day, "%Y-%m")) %>%
  group_by(clt_study_site, month) %>%
  summarise(
    num_referred = sum(num_referred, rm.na = TRUE),
    total_high_scores = sum(total_high_scores, rm.na = TRUE),
    referral_rate = (num_referred / total_high_scores) * 100,
    .groups = "drop"
  )

kable(monthly_referral_summary, caption = "Monthly Referral Rate by Facility",
      digits = 2)
```

\newpage

# 4. Telepsychiatry Referral Rate Per Facility (Per month)

We don't have many participants who need referral for telepsychiatry every day so we will calculate the referral rate per month only.

```{r, telepsych referral rate, echo = F, warning=F}
# Aggregate total women with PHQ9/GAD7 scores ??? 15 (Denominator)
phq9_high_scores_tele <- rct_ppw %>%
  filter((score_phq9 >= 15)| 
             (score_gad7 >=15)) %>%
  mutate(day = floor_date(clt_timestamp, "day")) %>%
  group_by(clt_study_site, day) %>%
  summarise(total_high_scores = n(),
            .groups = "drop")

# get the numerator from rct_ppw database
tele_referral <- rct_ppw %>% 
    filter(abs_phq_ref_tele == "Yes" | abs_gad7_ref_tele == "Yes") 
### this might not work (people might check one but not the other)

tele_referral <- tele_referral %>%
  mutate(day = floor_date(clt_timestamp, "day")) %>%
  group_by(clt_study_site, day) %>%
  summarise(num_referred = n(), .groups = "drop")

# Merge the two datasets
tele_referral <- left_join(tele_referral, phq9_high_scores_tele, 
                         by = c("clt_study_site" = "clt_study_site", "day" = "day"))
#there are missing data in the merged dataset. And it's impossible to have a total_high_scores bigger than num_referred.

#calculate referral rate
tele_referral <- tele_referral %>%
  mutate(referral_rate = num_referred / total_high_scores * 100)

# ggplot(tele_referral, aes(x = day, y = referral_rate, 
#                         color = clt_study_site)) +
#   geom_line() +
#   geom_point() +
#   labs(title = "Daily Referral Rate by Facility",
#        x = "Date", 
#        y = "Referral Rate (%)") +
#   theme_minimal() +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r, monthly telepsych referral rate table, echo = F, warning=F}
#make tele_referral have one row per day per facility
tele_referral <- tele_referral %>%
  distinct(clt_study_site, day, .keep_all = TRUE)

monthly_referral_summary_tele <- tele_referral %>%
  mutate(month = format(day, "%Y-%m")) %>%
  group_by(clt_study_site, month) %>%
  summarise(
    num_referred = sum(num_referred, rm.na = TRUE),
    total_high_scores = sum(total_high_scores, rm.na = TRUE),
    referral_rate = (num_referred / total_high_scores) * 100,
    .groups = "drop"
  )

kable(monthly_referral_summary_tele, caption = "Monthly Referral Rate by Facility",
      digits = 2)
```

\newpage

# 5. PM+ initiation rate per facility (Per month)

```{r, pm initiation rate, echo = F, warning=F}
#numerator is the number of participants who initiated PM+ [get from pm dataset]
pm_initiation <- pm %>%
    filter(pm_ptid == "Yes") %>%
    select(pm_facility, pm_date, pm_ptid, pm_session, pm_explain, pm_adv,
           pm_stress, pm_prob, pm_activ, pm_social, pm_stay, pm_nonresponse, pm_psycholops) %>% 
    mutate(month = format(pm_date, "%Y-%m")) 

#calculate the number of participants per facility per month and pm_session == "Pre-intervention PSYCHLOPS measurement"
pm_summary <- pm_initiation %>%
  filter(pm_session == "Pre-intervention PSYCHLOPS measurement") %>%
  group_by(pm_facility, month) %>%
  summarise(num_participants = n(), .groups = "drop")

#calculate the number of participants per facility per month and pm_session == "Session 1"
pm_summary_session1 <- pm_initiation %>%
  filter(pm_session == "Session 1") %>%
  group_by(pm_facility, month) %>%
  summarise(num_initiated = n(), .groups = "drop")

#denominator is the number of participants who are referred to PM+ [utilizing monthly_referral_summary]
pm_summary <- left_join(pm_summary, monthly_referral_summary, by = c("pm_facility" = "clt_study_site", "month" = "month"))


```
\newpage

# 6. PM+ completion rate per facility (Per month)

\newpage

# 7. Telepsychiatry initiation rate per facility (Per month)

\newpage

# 8. Frequency of conducting health talks & use of flipbook per facility (Per month)

```{r health talks, echo = F, warning=F}
# extract the health talk data from the daily closeout dataset
health_talks <- daily_closeout %>%
  select(rct_facility_name, rct_dcr_date, rct_health_talk, rct_flipbook) 
health_talks <- health_talks %>% 
    mutate(rct_health_talk = case_when(
      rct_health_talk == "Yes" ~ 1,
      rct_health_talk == "No" ~ 0,
      TRUE ~ NA_real_
    ),
    rct_flipbook = case_when(
      rct_flipbook == "Yes" ~ 1,
      rct_flipbook == "No" ~ 0,
      TRUE ~ NA_real_
    ))

# Aggregate the number of health talks and flipbook usage per facility per month
health_talks <- health_talks %>%
  mutate(month = format(rct_dcr_date, "%Y-%m")) %>%
  group_by(rct_facility_name, month) %>%
  summarise(
    num_health_talks = sum(rct_health_talk, na.rm = TRUE),
    num_flipbook = sum(rct_flipbook, na.rm = TRUE),
    percentage_flipbook = num_flipbook / num_health_talks * 100,
    .groups = "drop"
  )

kable(health_talks, caption = "Monthly Health Talks & Flipbook Usage by Facility")

```
