---
title: "IPMH_Audit_Feedback"
author: "Yuwei Wang"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, echo = F, include = F, warning=F}
rm(list = ls())

source("Audit and feedback script.R")
```

This script generates the audit and feedback report for each facility based on the calendar months. For the third audit and feedback session, we will report statistics from March 1st to May 31st. Data from the report should be abstracted for each facility and put into the slide template.

# 1. PHQ2 and GAD2 Screening Rate Per Facility (Per month & March-May Combined)

```{r, bar plots for each facility, echo = F, warning=F, fig.width = 6, fig.height = 4}
# Only rename columns for easier reference - no new columns created
plot_data_simple <- screening_rate_monthly %>%
  rename(
    screened = `Monthly screening`,
    anc_total = `Monthly ANC clients`,
    screening_rate = `PHQ2/GAD2 screening rate`
  )

# Loop through facilities
facilities <- unique(plot_data_simple$study_site)

for (facility in facilities) {
  facility_data <- plot_data_simple %>% filter(study_site == facility)
  
  p1 <- ggplot(facility_data, aes(x = month)) +
    # Screened portion (blue)
    geom_col(aes(y = pmin(100, (screened/anc_total) * 100)), 
             fill = "skyblue", width = 0.7) +
    # Unscreened portion (gray) - only if there are unscreened patients
    geom_col(aes(y = pmax(0, 100 - (screened/anc_total) * 100)), 
             fill = "gray80", width = 0.7,
             position = position_nudge(y = pmin(100, (facility_data$screened/facility_data$anc_total) * 100))) +
    
    # Labels for screened numbers and percentages
    geom_text(aes(y = pmin(50, (screened/anc_total) * 50),
                  label = paste0(screened, "\n(", round(pmin(100, (screened/anc_total) * 100), 1), "%)")),
              color = "white", fontface = "bold", size = 3.5) +
    
    # Total ANC labels above bars
    geom_text(aes(y = 105, label = paste0("ANC: ", anc_total)),
              size = 3) +
    
    labs(title = paste("PHQ2/GAD2 Screening Rate -", facility),
         x = "Month", y = "Screening Rate (%)") +
    scale_y_continuous(limits = c(0, 120), breaks = seq(0, 100, 20),
                       labels = paste0(seq(0, 100, 20), "%")) +
    theme_minimal(base_size = 13) +
    theme(panel.grid.minor.y = element_blank())
  
  print(p1)
}
```

```{r, monthly screening rate table, echo = F, warning=F}
kable(screening_rate_monthly, 
      caption = "Monthly PHQ2/GAD2 Screening Rate by Facility",
      digits = 2)
```

```{r, total screening rate table per facility, echo = F, warning=F}
kable(total_screening_rate, 
      caption = "March-May Combined PHQ2/GAD2 Screening Rate by Facility",
      digits = 2)
```

\newpage

# 2. PHQ9 and GAD7 Screening Rate Among Study Participants Per Facility (Per month & March-May Combined)

```{r, phq9 line plots for all facilities, include =F, echo = F, warning=F, fig.width=6, fig.height=4}
facilities <- unique(phq9_screening$clt_study_site)

for (facility in facilities) {
  facility_data <- phq9_screening_weekly %>% filter(clt_study_site == facility)
  
  p <- ggplot(facility_data, aes(x = week, y = `PHQ9/GAD7 screening rate`)) +
    geom_line(color = "blue") + 
    geom_point(color = "red") +
    labs(title = paste("Weekly PHQ9/GAD7 Screening Rate -", facility),
         x = "Date", 
         y = "PHQ9/GAD7 Screening Rate (%)") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          plot.title = element_text(size = 12)) +
    scale_x_date(date_breaks = "1 week", date_labels = "%Y-%m-%d") +
    scale_y_continuous(limits = c(0, 100))
  
  print(p)  # This will generate separate plots for each facility
}
```

```{r, monthly secondary screening rate table, echo = F, warning=F}
kable(phq9_screening_monthly, 
      caption = "PHQ9/GAD7 Monthly Screening Rate by Facility",
      digits = 2)
```

```{r, total secondary screening rate table, echo = F, warning=F}
kable(phq9_screening_total, 
      caption = "March-May Combined PHQ9/GAD7 Screening Rate by Facility",
      digits = 2)
```

\newpage

# 3. PM+ Referral Rate Per Facility (Per month & March-May Combined)

```{r, pm referral rate, echo = F, warning=F}
kable(pm_referral_monthly, 
      caption = "Monthly PM+ Referral Rate by Facility",
      digits = 2)

kable(pm_referral_total,
      caption = "March-May Combined PM+ Referral Rate by Facility",
      digits = 2)
```

\newpage

# 4. Telepsychiatry Referral Rate Per Facility (Per month & March-May Combined)

```{r, telepsych referral rate, echo = F, warning=F}
kable(monthly_referral_summary_tele, caption = "Monthly Telepsychiatry Referral Rate by Facility",
      digits = 2)

kable(total_referral_summary_tele, caption = "March-May Combined Telepsychiatry Referral Rate by Facility",
      digits = 2)
```

\newpage

# 5. PM+ initiation rate per facility (Per month & March-May Combined)

```{r, pm initiation rate, echo = F, warning=F}
kable(pm_summary_session1%>% select(1,2,3,4,7), 
      caption = "Monthly PM+ Initiation Rate (Session 1) by Facility",
      digits = 2)

kable(pm_initiation_all_merge_session1,
      caption = "March-May Combined PM+ Initiation Rate by Facility",
      digits = 2)
```
\newpage

# 6. PM+ completion rate per facility (Since Study Initiation)

```{r, pm completion rate, echo = F, warning=F}
kable(pm_completion_df, 
      caption = "PM+ Completion Rate by Facility Since Study Initiation",
      digits = 2)
```

\newpage

# 7. Telepsychiatry initiation rate per facility (Per month & March-May Combined)

```{r, telepsych initiation rate, echo = F, warning=F}
kable(telepsych_initiation_monthly, 
      caption = "Monthly Telepsychiatry Initiation Rate by Facility",
      digits = 2)

kable(telepsych_initiation_total,
      caption = "March-May Combined Telepsychiatry Initiation Rate by Facility",
      digits = 2)
```

\newpage

# 8. Frequency of conducting health talks & use of flipbook per facility (Per month & March-May Combined)

```{r health talks, echo = F, warning=F}
kable(health_talks_monthly, caption = "Monthly Health Talks & Flipbook Usage by Facility",
      digits = 2)
kable(total_health_talks, caption = "March-May Combined Health Talks & Flipbook Usage by Facility",
      digits = 2)
```
