---
title: "IPMH RCT IS Survey - HCW - 12 Months"
author: "Yuwei Wang"
date: "`r Sys.Date()`"
output:
  pdf_document
---

```{r setup, echo = F, include = F, warning=F}
rm(list = ls())

pacman::p_load(knitr, tidyverse, ggplot2, psych, janitor, dplyr, 
               openxlsx, gtsummary, kableExtra, ggrepel, UpSetR, funModeling, gt, mice) 
library(rstatix)
knitr::opts_chunk$set(fig.width = 10, fig.height = 12)

#Read data using datapull
source("REDCap_datapull.R")
is_survey_df <- rct_hcw
rm(list = setdiff(ls(), c("is_survey_df", "rct_hcw_consenting")))

is_survey_df <- is_survey_df %>%
    mutate(
        visit_type = case_when(
            grepl("pre", redcap_event_name, ignore.case = TRUE) ~ "Baseline",
            grepl("6-month", redcap_event_name) ~ "6 month",
            grepl("12-month", redcap_event_name) ~ "12 month",
            TRUE ~ "Other"
        )
    ) %>% 
    mutate(visit_type = factor(visit_type, levels = c("Baseline", "6 month", "12 month")))

#consenting database for cross-check 
rct_hcw_baseline <- rct_hcw_consenting %>%
    filter(is.na(redcap_repeat_instrument)) %>% 
    filter(redcap_event_name == "Pre-launch assessment (Arm 1: arm)")
    
rct_hcw_consenting_6mo <- rct_hcw_consenting %>%
    filter(is.na(redcap_repeat_instrument)) %>% 
    filter(redcap_event_name == "6-month assessment (Arm 1: arm)")

rct_hcw_consenting_12mo <- rct_hcw_consenting %>%
    filter(is.na(redcap_repeat_instrument)) %>% 
    filter(redcap_event_name == "12-month assessment (Arm 1: arm)")
```

## Health Care Workers Enrollment

Altogether, we currently have data for `r sum(grepl("pre", is_survey_df$redcap_event_name, ignore.case = TRUE))` participants for baseline, `r sum(grepl("6-month", is_survey_df$redcap_event_name))` participants for 6-month follow-up, and `r sum(grepl("12-month", is_survey_df$redcap_event_name))` participants for 12-month follow-up. 

```{r check ID, echo=F, message=FALSE, warning=FALSE, include= T}
# #12 month -----------
#check the IDs in the 12-month consenting database
consent_id_12mo <- rct_hcw_consenting_12mo %>%
    filter(grepl("12-month", redcap_event_name, ignore.case = TRUE)) %>%
    select(screen_id) %>%
    distinct()

#check the IDs in the survey database - 12-month
survey_id_12mo <- is_survey_df %>%
    filter(grepl("12-month", redcap_event_name, ignore.case = TRUE)) %>%
    select(pt_id) %>%
    distinct()

# #compare - 12-month
# setdiff(consent_id_12mo$screen_id, survey_id_12mo$pt_id)
# setdiff(survey_id_12mo$pt_id, consent_id_12mo$screen_id)

##Participant ID: 24090143 consented but does not have survey data? ##

#see how many participants we have three timepoints data
participant_timepoints <- is_survey_df %>%
    mutate(
        has_baseline = grepl("pre", redcap_event_name, ignore.case = TRUE),
        has_6month = grepl("6-month", redcap_event_name),
        has_12month = grepl("12-month", redcap_event_name)
    ) %>%
    group_by(pt_id, facility_id) %>%
    summarise(
        baseline = any(has_baseline),
        month_6 = any(has_6month),
        month_12 = any(has_12month),
        .groups = "drop"
    ) %>%
    mutate(
        baseline_and_6mo = baseline & month_6,
        all_three_timepoints = baseline & month_6 & month_12,
        newly_added_6mo = !baseline & (month_6),
        newly_added_12mo = !baseline & !month_6 & (month_12),
        missing_6mo = baseline & !month_6 & month_12
    )

# Summary table overall
participant_timepoints %>%
  summarise(
    `Baseline only`              = sum(baseline & !month_6 & !month_12),
    `Baseline + 6mo`             = sum(baseline & month_6 & !month_12),
    `Baseline + 6mo + 12mo`      = sum(baseline & month_6 & month_12),
    `Baseline + 12mo`            = sum(baseline & !month_6 & month_12),
    `6mo only`                   = sum(!baseline & month_6 & !month_12),
    `6mo + 12mo`                 = sum(!baseline & month_6 & month_12),
    `12mo only`                  = sum(!baseline & !month_6 & month_12)
  ) %>%
  pivot_longer(everything(),
               names_to  = "Category",
               values_to = "N") %>%
  kable(caption = "Participant Visit Patterns", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"))

## Summary table by facility
# participant_timepoints %>%
#   group_by(facility_id) %>%
#   summarise(
#     `Baseline only`              = sum(baseline & !month_6 & !month_12),
#     `Baseline + 6mo`             = sum(baseline & month_6 & !month_12),
#     `Baseline + 6mo + 12mo`      = sum(baseline & month_6 & month_12),
#     `Baseline + 12mo`            = sum(baseline & !month_6 & month_12),
#     `6mo only`                   = sum(!baseline & month_6 & !month_12),
#     `6mo + 12mo`                 = sum(!baseline & month_6 & month_12),
#     `12mo only`                  = sum(!baseline & !month_6 & month_12),
#     .groups = "drop"
#   ) %>%
#   kable(caption  = "Participant Visit Patterns by Facility",
#         booktabs = TRUE) %>%
#   kable_styling(latex_options = c("striped", "hold_position", "scale_down"))
```

```{r, arm, echo=F, message=FALSE, warning=FALSE}
is_survey_df <- is_survey_df %>%
    mutate(
        facility_num = str_extract(facility_id, "^[0-9]+"),  # Extracts only the leading number
        arm = case_when(
            facility_num %in% c("01", "03", "04", "07", "09", "13", "16", "17", "19", "22") ~ "Intervention",
            TRUE ~ "Control"
        ))

# extracts "Arm x" from redcap_event_name
is_survey_df$arm_redcap <- str_extract(is_survey_df$redcap_event_name, "Arm [0-9]+")

arm_labels <- c(
  "Arm 1" = "Lay Provider",
  "Arm 2" = "In-charge",
  "Arm 3" = "Nurse",
  "Arm 4" = "Lay Provider ",
  "Arm 5" = "In-charge ",
  "Arm 6" = "Nurse "
)

is_survey_df %>%
  filter(grepl("12-month", redcap_event_name)) %>%
  mutate(arm_redcap = recode(arm_redcap, !!!arm_labels)) %>%
  count(arm_redcap, facility_id) %>%
  pivot_wider(names_from  = arm_redcap,
              values_from = n,
              values_fill = 0) %>%
  select(facility_id, 
         `Lay Provider`, `In-charge`, `Nurse`,
         `Lay Provider `, `In-charge `, `Nurse `) %>%
  kable(caption  = "Number of Participants by Arm and Facility (12 months follow-up)",
        booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                full_width    = FALSE) %>%
  add_header_above(c(" " = 1, 
                     "Intervention" = 3, 
                     "Control" = 3))

```

\newpage

## Demographic Summary for 12 months

```{r, Basic Demographic Summary, echo=FALSE, message=FALSE, warning=FALSE}
demo_baseline <- is_survey_df %>% 
    filter(visit_type == "Baseline")
demo_6month <- is_survey_df %>%
    filter(visit_type == "6 month")
demo_12month <- is_survey_df %>%
    filter(visit_type == "12 month")

# Participants with 12m visit only
ids_12m <- demo_12month$pt_id

# Get demographics from earliest available visit
demo_12m_participants <- bind_rows(demo_baseline, 
                                   demo_6month, demo_12month) %>%
  filter(pt_id %in% ids_12m) %>%
  mutate(visit_order = case_when(
    visit_type == "Baseline" ~ 1,
    visit_type == "6 month"  ~ 2,
    visit_type == "12 month" ~ 3
  )) %>%
  arrange(pt_id, visit_order) %>%
  group_by(pt_id) %>%
  slice(1) %>%
  ungroup() %>%
  select(-visit_order)

demo_12m_participants <- demo_12m_participants %>% 
  select(arm, part_id,  pt_type, facility_id, calculated_pt_id, 
         dob_uk, age, cal_age, sex, education, 
         dpt___1, dpt___2, dpt___3, dpt___4, dpt___5, dpt___6, dpt___7, 
          job_arm14___1,  job_arm14___2,  job_arm25___1,  job_arm25___2, 
         job_arm25___3, job_arm25___4,  job_arm25___5,  job_arm25___6, 
         job_arm25___7, job_arm36___1,  job_arm36___2,  job_arm36___3,  
         job_arm7___1, job_arm7___2,
          monthsjob, monthswork, terms, care,  wlwh, monthscare,
          hrscare, wlwh, demographic_complete)%>% 
    filter(demographic_complete == "Complete") %>% 
    mutate(age_final = case_when(
        dob_uk == "Yes" ~ floor(as.numeric(cal_age)),
        dob_uk == "No" ~ as.numeric(age),
        TRUE ~ NA_real_))

demo_12m_participants <- demo_12m_participants %>% 
  #   mutate(sex = dplyr::recode(sex, 
  #                              "1" = "Male",
  #                              "2" = "Female")) %>% 
  # mutate(education = dplyr::recode(education, 
  #                                      "1" = "No schooling completed",
  #                                      "2" = "Primary school",
  #                                      "3" = "Secondary school", 
  #                                      "4" = "Diploma", 
  #                                      "5" = "Bachelor's degree or higher degree"),
  #        education = fct_relevel(education,
  #                                "Diploma", "Bachelor's degree or higher degree",
  #                                "Secondary school", "Primary school")) %>%
  mutate(designation = dplyr::case_when(
      job_arm14___1 == "Checked" ~ "HTS counsellor",
      job_arm14___2 == "Checked" ~ "Mentor Mother",
      job_arm25___1 == "Checked" ~ "Medical officer",
      job_arm25___2 == "Checked" ~ "Obstetrician/gynaecologist",
      job_arm25___3 == "Checked" ~ "Clinical Officer",
      job_arm25___4 == "Checked" ~ "Nurses",
      job_arm25___6 == "Checked" ~  "Other social worker",
      job_arm25___7 == "Checked" ~ "Others",
      job_arm36___1 == "Checked" ~ "Medical officer",
      job_arm36___2 == "Checked" ~ "Clinical Officer",
      job_arm36___3 == "Checked" ~ "Nurses",
      job_arm7___1 == "Checked" ~ "Psychologist",
      job_arm7___2 == "Checked" ~ "Psychiatrist",
      TRUE ~ NA_character_)) %>%
  # mutate(care = dplyr::recode(care, 
  #                               "0" = "No",
  #                               "1" = "Yes"),
  #          wlwh = dplyr::recode(wlwh,
  #                               "0" = "No",
  #                               "1" = "Yes")) %>% 
  #   mutate(terms = dplyr::recode(terms, 
  #                                "1" = "Permanent and pensionable", 
  #                                "2" = "Contract",
  #                                "3" = "Volunteer", 
  #                                "4" = "Other"),
  #          terms = fct_relevel(terms,
  #                                "Contract", "Permanent and pensionable", 
  #                                "Volunteer", "Other")) %>% 
  mutate(monthsjob = as.numeric(monthsjob, monthswork,  monthscare, hrscare)#,
         # pt_type = recode(pt_type,
         #                  "22" = "Lay providers",
         #                  "23" = "Facility-in-charge",
         #                  "24" = "Nurses/COs/MOs",
         #                  "25" = "Psychiatrists/Psychologists")
         )%>% 
  mutate(yearjob = monthsjob/12) %>% 
    mutate(yearwork = monthswork/12) %>% 
    mutate(yearcare = monthscare/12)

# basic demo table
demo_12m_participants %>% tbl_summary(
    by = "arm",
    include=c(arm, age_final, sex, education, dpt___1, dpt___2, 
            dpt___3, dpt___4, dpt___5, dpt___6, dpt___7,
            designation,  yearjob, yearwork, yearcare, 
            hrscare, terms, care,  wlwh),
    label = list(age_final ~ "Age (Years)",
               sex ~ "Gender",
               education ~ "Education level",
               dpt___1 ~ "Working in antenatal care",
               dpt___2 ~ "Working in postnatal care",
               dpt___3 ~ "Working in immunization clinic",
               dpt___4 ~ "Working in PMTCT",
               dpt___5 ~ "Working in family planning clinic",
               dpt___6 ~ " Psychological/Psychiatric care",
               dpt___7 ~ "Working in other department",
               designation ~ "Current Designation",
               yearjob ~ "Current job duration (Years)",
               yearwork ~ "Duration in the facility (Years)",
               terms ~ "Terms of engagement in the facility",
               care ~ "Offering care to perinatal women (Yes)",
               yearcare ~ "Duration of offering care to PW in the facility (Years)",
               hrscare ~ "Hours/week taking care of PW in the facility", 
               wlwh ~ "Currently providing care to PW living with HIV (Yes)"),
    missing = "no",
    digits = list(all_continuous() ~ 1), 
    type = list(age_final ~ "continuous", 
              yearjob ~ "continuous",
              yearwork ~ "continuous", 
              yearcare ~ "continuous", 
              hrscare ~ "continuous"),
  statistic = list(all_continuous() ~ "{mean} ({SD})")) %>% 
     add_overall() %>% 
     add_p() %>% 
  bold_labels() %>%
      as_kable_extra(
    caption  = "Baseline Characteristics of 12-Month Participants",
    booktabs = TRUE
  ) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"),
    full_width    = FALSE
  )
```

```{r Participants Interviewed by cadre per facility, echo=FALSE, message=FALSE, warning=FALSE, include=F}
suveys_done <- is_survey_df %>% 
    select(visit_type, pt_id, facility_id, pt_type) %>% 
    group_by(visit_type, facility_id, pt_type) %>%
  summarise(count = n(), .groups = "drop")%>%
  pivot_wider(names_from = pt_type, values_from = count, values_fill = 0)%>%
  mutate(`Total_Facility` = rowSums(across(where(is.numeric)))) %>%  # Add row totals
  arrange(visit_type, facility_id) %>%  # Arrange by visit_type first, then facility
    bind_rows(summarise(., across(where(is.numeric), sum), facility_id = "Total"))%>%  # Add column totals
    gt() %>%
  tab_header(
    title = "Summary of HCWs Surveyed by Facility",
    subtitle = "Showing counts of each HCWs type per facility"
  ) %>%
  cols_label(
    facility_id = "Facility",
    Total_Facility = "Total"
  ) %>%
  tab_options(
    table.font.size = px(12)
  )
suveys_done
```

\newpage

## Intervention Characteristics 

A higher score indicates a more positive perception of the intervention characteristics. This is measured at both 6 months and 12 months in the intervention arm only.

```{r intervention_characteristics, echo=FALSE, message=FALSE, warning=FALSE}
intervention_df <- is_survey_df %>% 
    select(visit_type, pt_id, facility_id, pt_type, arm, starts_with("adapt_"), 
           starts_with("complex_"), starts_with("trial_"), 
           intervention_characteristic_complete) %>% 
    filter(arm == "Intervention") 

intervention_df <- intervention_df %>%
    filter(!is.na(pt_type)) %>%  # Remove rows where pt_type is NA
    mutate(pt_type = droplevels(factor(pt_type))) %>% 
    filter(!is.na(facility_id)) %>% 
    mutate(facility_id = droplevels(factor(facility_id)))

intervention_df <- intervention_df %>% 
    mutate(across(c(starts_with("adapt_"), 
           starts_with("complex_"), starts_with("trial_")), ~ case_when(
        . == "1: Completely disagree" ~ 1,
        . == "2: Disagree" ~ 2,
        . == "3: Neither agree nor disagree" ~ 3,
        . == "4: Agree" ~ 4,
        . == "5: Completely agree" ~ 5,
        . == "Prefer not to answer" ~ NA_real_,  # Convert to NA
        TRUE ~ as.numeric(as.character(.))  # Ensure numeric conversion
    ))) 

#no reverse coding

intervention_df <- intervention_df %>%
    mutate(
        adapt = rowMeans(select(., starts_with("adapt_")), na.rm = TRUE),
        complex = rowMeans(select(., starts_with("complex_")), na.rm = TRUE),
        trial = rowMeans(select(., starts_with("trial_")), na.rm = TRUE)
    )
```

```{r, continuous, echo=FALSE, message=FALSE, warning=FALSE}
# by pt_type at 6 months
intervention_df %>% 
  filter(grepl("6 month", visit_type)) %>%
  tbl_summary(
    by      = pt_type,
    include = c(adapt, complex, trial),
    type    = list(adapt   ~ "continuous",
                   complex ~ "continuous",
                   trial   ~ "continuous"),
    missing = "no"
  ) %>%
  add_overall() %>%
  add_p() %>%
  bold_labels() %>%
  as_kable_extra(
    caption  = "Intervention Characteristics (6 month) Summary by Participant Type",
    booktabs = TRUE
  ) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"),
    full_width    = FALSE
  )

# ---- By facility (6 month) ----
# intervention_df %>%
#   filter(grepl("6 month", visit_type)) %>%
#   tbl_summary(
#     by      = facility_id,
#     include = c(adapt, complex, trial),
#     type    = list(adapt   ~ "continuous",
#                    complex ~ "continuous",
#                    trial   ~ "continuous"),
#     missing = "no"
#   ) %>%
#   add_overall() %>%
#   add_p() %>%
#   bold_labels() %>%
#   as_kable_extra(
#     caption  = "Intervention Characteristics (6 month) Summary by Facility",
#     booktabs = TRUE
#   ) %>%
#   kable_styling(
#     latex_options = c("striped", "hold_position", "scale_down"),
#     full_width    = FALSE
#   )

# ---- By pt_type (12 month) ----
intervention_df %>%
  filter(grepl("12 month", visit_type)) %>%
  tbl_summary(
    by      = pt_type,
    include = c(adapt, complex, trial),
    type    = list(adapt   ~ "continuous",
                   complex ~ "continuous",
                   trial   ~ "continuous"),
    missing = "no"
  ) %>%
  add_overall() %>%
  add_p() %>%
  bold_labels() %>%
  as_kable_extra(
    caption  = "Intervention Characteristics (12 month) Summary by Participant Type",
    booktabs = TRUE
  ) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"),
    full_width    = FALSE
  )

# ---- By facility (12 month) ----
# intervention_df %>%
#   filter(grepl("12 month", visit_type)) %>%
#   tbl_summary(
#     by      = facility_id,
#     include = c(adapt, complex, trial),
#     type    = list(adapt   ~ "continuous",
#                    complex ~ "continuous",
#                    trial   ~ "continuous"),
#     missing = "no"
#   ) %>%
#   add_overall() %>%
#   add_p() %>%
#   bold_labels() %>%
#   as_kable_extra(
#     caption  = "Intervention Characteristics (6 month) Summary by Facility",
#     booktabs = TRUE
#   ) %>%
#   kable_styling(
#     latex_options = c("striped", "hold_position", "scale_down"),
#     full_width    = FALSE
#   )

# ---- 6m vs 12m comparison ----
intervention_df %>%
  filter(grepl("6 month|12 month", visit_type)) %>%
  mutate(visit_type = factor(visit_type, 
                             levels = c("6 month", "12 month"))) %>%
  tbl_summary(
    by      = visit_type,
    include = c(adapt, complex, trial),
    type    = list(adapt   ~ "continuous",
                   complex ~ "continuous",
                   trial   ~ "continuous"),
    missing = "no"
  ) %>%
  add_overall() %>%
  add_p() %>%
  bold_labels() %>%
  as_kable_extra(
    caption  = "Intervention Characteristics: 6 Month vs 12 Month Comparison",
    booktabs = TRUE
  ) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"),
    full_width    = FALSE
  )

# Paired Wilcoxon test for participants with both 6m and 12m data
ids_both_6m_12m <- intervention_df %>%
  filter(grepl("6 month|12 month", visit_type)) %>%
  group_by(pt_id) %>%
  summarise(
    has_6m = any(grepl("6 month", visit_type)),
    has_12m = any(grepl("12 month", visit_type)),
    .groups = "drop"
  ) %>%
  filter(has_6m & has_12m) %>%
  pull(pt_id)

wide_df <- intervention_df %>%
  filter(grepl("6 month|12 month", visit_type)) %>%
  filter(pt_id %in% ids_both_6m_12m) %>%
  select(pt_id, visit_type, adapt, complex, trial) %>%
  pivot_wider(names_from  = visit_type,
              values_from = c(adapt, complex, trial))

paired_results <- tibble(
  Outcome = c("Adapt", "Complex", "Trial"),
  Median_6m = c(median(wide_df$`adapt_6 month`,   na.rm = TRUE),
                median(wide_df$`complex_6 month`,  na.rm = TRUE),
                median(wide_df$`trial_6 month`,    na.rm = TRUE)),
  Median_12m = c(median(wide_df$`adapt_12 month`,  na.rm = TRUE),
                 median(wide_df$`complex_12 month`, na.rm = TRUE),
                 median(wide_df$`trial_12 month`,   na.rm = TRUE)),
  Median_diff = c(
    median(wide_df$`adapt_12 month`   - wide_df$`adapt_6 month`,   na.rm = TRUE),
    median(wide_df$`complex_12 month` - wide_df$`complex_6 month`, na.rm = TRUE),
    median(wide_df$`trial_12 month`   - wide_df$`trial_6 month`,   na.rm = TRUE)
  )
) %>%
  mutate(
    wilcox_test = list(
      wilcox.test(wide_df$`adapt_6 month`,   wide_df$`adapt_12 month`,
                  paired = TRUE, conf.int = TRUE),
      wilcox.test(wide_df$`complex_6 month`, wide_df$`complex_12 month`,
                  paired = TRUE, conf.int = TRUE),
      wilcox.test(wide_df$`trial_6 month`,   wide_df$`trial_12 month`,
                  paired = TRUE, conf.int = TRUE)
    ),
    W_stat  = map_dbl(wilcox_test, ~ .x$statistic),
    p_value = map_dbl(wilcox_test, ~ .x$p.value),
    CI_lo   = map_dbl(wilcox_test, ~ .x$conf.int[1]),
    CI_hi   = map_dbl(wilcox_test, ~ .x$conf.int[2])
  ) %>%
  select(-wilcox_test) %>%
  mutate(
    across(c(Median_6m, Median_12m, Median_diff, W_stat, CI_lo, CI_hi),
           ~ round(.x, 2)),
    p_value = round(p_value, 3),
    CI      = sprintf("(%.2f, %.2f)", CI_lo, CI_hi)
  ) %>%
  select(Outcome, Median_6m, Median_12m, Median_diff, CI, W_stat, p_value) %>%
  rename(
    `Outcome`           = Outcome,
    `Median (6mo)`      = Median_6m,
    `Median (12mo)`     = Median_12m,
    `Median Difference` = Median_diff,
    `95% CI`            = CI,
    `W-statistic`       = W_stat,
    `P-value`           = p_value
  )

paired_results %>%
  kable(
    caption  = "Paired Wilcoxon Test Results: 6 Month vs 12 Month (participants with both timepoints)",
    booktabs = TRUE,
    align    = "lcccccc"
  ) %>%
  kable_styling(
    latex_options = c("striped", "hold_position"),
    full_width    = FALSE
  )
```

\newpage

## Acceptability, appropriateness, and feasibility

A higher score indicates a more positive perception of the intervention's acceptability, appropriateness, and feasibility. This is measured at baseline, 6 months, and 12 months in the intervention arm only.

### IPMH Acceptability

```{r Acceptability, echo=FALSE, message=FALSE}
acceptability <- is_survey_df %>% 
  select(pt_id, pt_type, facility_id, arm, aim_1, aim_2,
         aim_3, aim_4, visit_type) %>% 
  filter(arm == "Intervention") %>% 
  filter(!is.na(pt_type)) %>%
  mutate(pt_type = droplevels(factor(pt_type))) %>% 
  filter(!is.na(facility_id)) %>% 
  mutate(facility_id = droplevels(factor(facility_id))) %>%
  # Recode first
  mutate(across(c(starts_with("aim_")), ~ case_when(
    . == "Completely disagree"        ~ 1,
    . == "Disagree"                   ~ 2,
    . == "Neither agree nor disagree" ~ 3,
    . == "Agree"                      ~ 4,
    . == "Completely agree"           ~ 5,
    . == "Prefer not to answer"       ~ NA_real_,
    TRUE                              ~ NA_real_
  ))) %>%
  # Then calculate total
  mutate(
    aim_total = rowMeans(select(., starts_with("aim_")), na.rm = TRUE)
  )

# Participants with all 3 timepoints
ids_all_three <- acceptability %>%
  group_by(pt_id) %>%
  summarise(
    has_baseline = any(grepl("Baseline", visit_type, ignore.case = TRUE)),
    has_6m       = any(grepl("6 month", visit_type)),
    has_12m      = any(grepl("12 month", visit_type))
  ) %>%
  filter(has_baseline & has_6m & has_12m) %>%
  pull(pt_id)

# table for each time points
acceptability %>%
  mutate(visit_type = factor(visit_type,
                             levels = c("Baseline", "6 month", "12 month"))) %>%
  tbl_summary(
    by      = visit_type,
    include = c(aim_1, aim_2, aim_3, aim_4, aim_total),
    label   = list(aim_1     ~ "IPMH meets my approval",
                   aim_2     ~ "IPMH is appealing to me",
                   aim_3     ~ "I like IPMH",
                   aim_4     ~ "I welcome IPMH",
                   aim_total ~ "Acceptability total score"),
    type    = list(aim_1     ~ "continuous",
                   aim_2     ~ "continuous",
                   aim_3     ~ "continuous",
                   aim_4     ~ "continuous",
                   aim_total ~ "continuous"),
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    missing = "no"
  ) %>%
  bold_labels() %>% add_overall() %>% add_p() %>%
  as_kable_extra(
    caption  = "Acceptability Scores Across Timepoints",
    booktabs = TRUE
  ) %>%
  kable_styling(
    latex_options = c("striped", "hold_position"),
    full_width    = FALSE
  )

# Friedman test for aim_total across 3 timepoints
ids_complete <- acceptability %>%
  filter(pt_id %in% ids_all_three) %>%
  group_by(pt_id) %>%
  summarise(any_na = any(is.na(aim_total)), .groups = "drop") %>%
  filter(!any_na) %>%
  pull(pt_id)

acceptability %>%
  filter(pt_id %in% ids_complete) %>%
  mutate(visit_type = factor(visit_type,
                             levels = c("Baseline", "6 month", "12 month"))) %>%
  friedman_test(aim_total ~ visit_type | pt_id) %>%
  mutate(p = round(p, 3),
         statistic = round(statistic, 3)) %>%
  rename(
    `Outcome`   = .y.,
    `N`         = n,
    `Statistic` = statistic,
    `df`        = df,
    `P-value`   = p,
    `Method`    = method
  ) %>%
  kable(
    caption  = "Friedman Test: Acceptability Scores Across Timepoints",
    booktabs = TRUE,
    align    = "lccccc"
  ) %>%
  kable_styling(
    latex_options = c("striped", "hold_position"),
    full_width    = FALSE
  )


# #by py_type - 12 months
# acceptability %>%
#   filter(grepl("12 month", visit_type)) %>%
#   tbl_summary(
#     by        = pt_type,
#     include   = c(aim_1, aim_2, aim_3, aim_4, aim_total),
#     label     = list(aim_1     ~ "IPMH meets my approval",
#                      aim_2     ~ "IPMH is appealing to me",
#                      aim_3     ~ "I like IPMH.",
#                      aim_4     ~ "I welcome IPMH",
#                      aim_total ~ "Acceptability total score"),
#     type      = list(aim_1     ~ "continuous",
#                      aim_2     ~ "continuous",
#                      aim_3     ~ "continuous",
#                      aim_4     ~ "continuous",
#                      aim_total ~ "continuous"),
#     statistic = list(all_continuous() ~ "{mean} ({sd})"),
#     missing   = "no"
#   ) %>%
#   add_overall() %>%
#   add_p() %>%
#   bold_labels() %>%
#   as_kable_extra(
#     caption  = "IPMH Acceptability by Participant Type at 12 months",
#     booktabs = TRUE
#   ) %>%
#   kable_styling(
#     latex_options = c("striped", "hold_position", "scale_down"),
#     full_width    = FALSE
#   )
    
# #by facility at 12 months
# acceptability %>%
#   filter(grepl("12 month", visit_type)) %>%
#   tbl_summary(
#     by        = facility_id,
#     include   = c(aim_1, aim_2, aim_3, aim_4, aim_total),
#     label     = list(aim_1     ~ "IPMH meets my approval",
#                      aim_2     ~ "IPMH is appealing to me",
#                      aim_3     ~ "I like IPMH.",
#                      aim_4     ~ "I welcome IPMH",
#                      aim_total ~ "Acceptability total score"),
#     type      = list(aim_1     ~ "continuous",
#                      aim_2     ~ "continuous",
#                      aim_3     ~ "continuous",
#                      aim_4     ~ "continuous",
#                      aim_total ~ "continuous"),
#     statistic = list(all_continuous() ~ "{mean} ({sd})"),
#     missing   = "no"
#   ) %>%
#   add_overall() %>%
#   add_p() %>%
#   bold_labels() %>%
#   as_kable_extra(
#     caption  = "IPMH Acceptability by Participant Type at 12 months",
#     booktabs = TRUE
#   ) %>%
#   kable_styling(
#     latex_options = c("striped", "hold_position", "scale_down"),
#     full_width    = FALSE
#   )
```

### IPMH Appropriateness

```{r appropriateness, echo=FALSE, message=FALSE, warning=FALSE}
appropriateness <- is_survey_df %>% 
  select(pt_id, pt_type, facility_id, arm, iam_1, iam_2,
         iam_3, iam_4, visit_type) %>% 
  filter(arm == "Intervention") %>% 
  filter(!is.na(pt_type)) %>%
  mutate(pt_type = droplevels(factor(pt_type))) %>% 
  filter(!is.na(facility_id)) %>% 
  mutate(facility_id = droplevels(factor(facility_id))) %>%
  mutate(across(c(starts_with("iam_")), ~ case_when(
    . == "Completely disagree"        ~ 1,
    . == "Disagree"                   ~ 2,
    . == "Neither agree nor disagree" ~ 3,
    . == "Agree"                      ~ 4,
    . == "Completely agree"           ~ 5,
    . == "Prefer not to answer"       ~ NA_real_,
    TRUE                              ~ NA_real_
  ))) %>%
  mutate(
    iam_total = rowMeans(select(., starts_with("iam_")), na.rm = TRUE)
  )

# Descriptive table by pt_type at 12 months
appropriateness %>%
  filter(grepl("12 month", visit_type)) %>%
  tbl_summary(
    by        = pt_type,
    include   = c(iam_1, iam_2, iam_3, iam_4, iam_total),
    label     = list(iam_1     ~ "IPMH seems fitting",
                     iam_2     ~ "IPMH seems suitable",
                     iam_3     ~ "IPMH seems applicable",
                     iam_4     ~ "IPMH seems like a good match",
                     iam_total ~ "Appropriateness total score"),
    type      = list(iam_1     ~ "continuous",
                     iam_2     ~ "continuous",
                     iam_3     ~ "continuous",
                     iam_4     ~ "continuous",
                     iam_total ~ "continuous"),
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    missing   = "no"
  ) %>%
  add_overall() %>%
  add_p() %>%
  bold_labels() %>%
  as_kable_extra(
    caption  = "IPMH Appropriateness by Participant Type at 12 months",
    booktabs = TRUE
  ) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"),
    full_width    = FALSE
  )

# Friedman test across timepoints
ids_all_three_iam <- appropriateness %>%
  group_by(pt_id) %>%
  summarise(
    has_baseline = any(grepl("Baseline", visit_type, ignore.case = TRUE)),
    has_6m       = any(grepl("6 month", visit_type)),
    has_12m      = any(grepl("12 month", visit_type))
  ) %>%
  filter(has_baseline & has_6m & has_12m) %>%
  pull(pt_id)

ids_complete_iam <- appropriateness %>%
  filter(pt_id %in% ids_all_three_iam) %>%
  group_by(pt_id) %>%
  summarise(any_na = any(is.na(iam_total)), .groups = "drop") %>%
  filter(!any_na) %>%
  pull(pt_id)

appropriateness %>%
  filter(pt_id %in% ids_complete_iam) %>%
  mutate(visit_type = factor(visit_type,
                             levels = c("Baseline", "6 month", "12 month"))) %>%
  friedman_test(iam_total ~ visit_type | pt_id) %>%
  mutate(p         = round(p, 3),
         statistic = round(statistic, 3)) %>%
  rename(
    `Outcome`   = .y.,
    `N`         = n,
    `Statistic` = statistic,
    `df`        = df,
    `P-value`   = p,
    `Method`    = method
  ) %>%
  kable(
    caption  = "Friedman Test: Appropriateness Scores Across Timepoints",
    booktabs = TRUE,
    align    = "lccccc"
  ) %>%
  kable_styling(
    latex_options = c("striped", "hold_position"),
    full_width    = FALSE
  )

# # ---- By pt_type ----
# appropriateness %>%
#   filter(grepl("12 month", visit_type)) %>%
#   tbl_summary(
#     by        = pt_type,
#     include   = c(iam_1, iam_2, iam_3, iam_4, iam_total),
#     label     = list(iam_1     ~ "IPMH seems fitting",
#                      iam_2     ~ "IPMH seems suitable",
#                      iam_3     ~ "IPMH seems applicable",
#                      iam_4     ~ "IPMH seems like a good match",
#                      iam_total ~ "Appropriateness total score"),
#     type      = list(iam_1     ~ "continuous",
#                      iam_2     ~ "continuous",
#                      iam_3     ~ "continuous",
#                      iam_4     ~ "continuous",
#                      iam_total ~ "continuous"),
#     statistic = list(all_continuous() ~ "{mean} ({sd})"),
#     missing   = "no"
#   ) %>%
#   add_overall() %>%
#   add_p() %>%
#   bold_labels() %>%
#   as_kable_extra(
#     caption  = "IPMH Appropriateness by Participant Type at 12 months",
#     booktabs = TRUE
#   ) %>%
#   kable_styling(
#     latex_options = c("striped", "hold_position", "scale_down"),
#     full_width    = FALSE
#   )

# # ---- By facility_id ----
# appropriateness %>%
#   filter(grepl("12 month", visit_type)) %>%
#   tbl_summary(
#     by        = facility_id,
#     include   = c(iam_1, iam_2, iam_3, iam_4, iam_total),
#     label     = list(iam_1     ~ "IPMH seems fitting",
#                      iam_2     ~ "IPMH seems suitable",
#                      iam_3     ~ "IPMH seems applicable",
#                      iam_4     ~ "IPMH seems like a good match",
#                      iam_total ~ "Appropriateness total score"),
#     type      = list(iam_1     ~ "continuous",
#                      iam_2     ~ "continuous",
#                      iam_3     ~ "continuous",
#                      iam_4     ~ "continuous",
#                      iam_total ~ "continuous"),
#     statistic = list(all_continuous() ~ "{mean} ({sd})"),
#     missing   = "no"
#   ) %>%
#   add_overall() %>%
#   add_p() %>%
#   bold_labels() %>%
#   as_kable_extra(
#     caption  = "IPMH Appropriateness by Facility at 12 months",
#     booktabs = TRUE
#   ) %>%
#   kable_styling(
#     latex_options = c("striped", "hold_position", "scale_down"),
#     full_width    = FALSE
#   )
```

\newpage 

### IPMH Feasibility

```{r Feasibility, echo=FALSE, message=FALSE, warning=FALSE}
feasibility <- is_survey_df %>% 
  select(pt_id, pt_type, facility_id, arm, fim_1, fim_2,
         fim_3, fim_4, visit_type) %>% 
  filter(arm == "Intervention") %>% 
  filter(!is.na(pt_type)) %>%
  mutate(pt_type = droplevels(factor(pt_type))) %>% 
  filter(!is.na(facility_id)) %>% 
  mutate(facility_id = droplevels(factor(facility_id))) %>%
  mutate(across(c(starts_with("fim_")), ~ case_when(
    . == "Completely disagree"        ~ 1,
    . == "Disagree"                   ~ 2,
    . == "Neither agree nor disagree" ~ 3,
    . == "Agree"                      ~ 4,
    . == "Completely agree"           ~ 5,
    . == "Prefer not to answer"       ~ NA_real_,
    TRUE                              ~ NA_real_
  ))) %>%
  mutate(
    fim_total = rowMeans(select(., starts_with("fim_")), na.rm = TRUE)
  )

# --- Descriptive table by pt_type at 12 months
feasibility %>%
  filter(grepl("12 month", visit_type)) %>%
  tbl_summary(
    by        = pt_type,
    include   = c(fim_1, fim_2, fim_3, fim_4, fim_total),
    label     = list(fim_1     ~ "IPMH seems implementable",
                     fim_2     ~ "IPMH seems possible",
                     fim_3     ~ "IPMH seems doable",
                     fim_4     ~ "IPMH seems easy to use",
                     fim_total ~ "Feasibility total score"),
    type      = list(fim_1     ~ "continuous",
                     fim_2     ~ "continuous",
                     fim_3     ~ "continuous",
                     fim_4     ~ "continuous",
                     fim_total ~ "continuous"),
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    missing   = "no"
  ) %>%
  add_overall() %>%
  add_p() %>%
  bold_labels() %>%
  as_kable_extra(
    caption  = "IPMH Feasibility by Participant Type at 12 months",
    booktabs = TRUE
  ) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"),
    full_width    = FALSE
  )

# ---- Friedman test across timepoints ----
ids_all_three_fim <- feasibility %>%
  group_by(pt_id) %>%
  summarise(
    has_baseline = any(grepl("Baseline", visit_type, ignore.case = TRUE)),
    has_6m       = any(grepl("6 month", visit_type)),
    has_12m      = any(grepl("12 month", visit_type))
  ) %>%
  filter(has_baseline & has_6m & has_12m) %>%
  pull(pt_id)

ids_complete_fim <- feasibility %>%
  filter(pt_id %in% ids_all_three_fim) %>%
  group_by(pt_id) %>%
  summarise(any_na = any(is.na(fim_total)), .groups = "drop") %>%
  filter(!any_na) %>%
  pull(pt_id)

feasibility %>%
  filter(pt_id %in% ids_complete_fim) %>%
  mutate(visit_type = factor(visit_type,
                             levels = c("Baseline", "6 month", "12 month"))) %>%
  friedman_test(fim_total ~ visit_type | pt_id) %>%
  mutate(p         = round(p, 3),
         statistic = round(statistic, 3)) %>%
  rename(
    `Outcome`   = .y.,
    `N`         = n,
    `Statistic` = statistic,
    `df`        = df,
    `P-value`   = p,
    `Method`    = method
  ) %>%
  kable(
    caption  = "Friedman Test: Feasibility Scores Across Timepoints",
    booktabs = TRUE,
    align    = "lccccc"
  ) %>%
  kable_styling(
    latex_options = c("striped", "hold_position"),
    full_width    = FALSE
  )

# # ---- By pt_type ----
# feasibility %>%
#   filter(grepl("12 month", visit_type)) %>%
#   tbl_summary(
#     by        = pt_type,
#     include   = c(fim_1, fim_2, fim_3, fim_4, fim_total),
#     label     = list(fim_1     ~ "IPMH seems implementable",
#                      fim_2     ~ "IPMH seems possible",
#                      fim_3     ~ "IPMH seems doable",
#                      fim_4     ~ "IPMH seems easy to use",
#                      fim_total ~ "Feasibility total score"),
#     type      = list(fim_1     ~ "continuous",
#                      fim_2     ~ "continuous",
#                      fim_3     ~ "continuous",
#                      fim_4     ~ "continuous",
#                      fim_total ~ "continuous"),
#     statistic = list(all_continuous() ~ "{mean} ({sd})"),
#     missing   = "no"
#   ) %>%
#   add_overall() %>%
#   add_p() %>%
#   bold_labels() %>%
#   as_kable_extra(
#     caption  = "IPMH Feasibility by Participant Type at 12 months",
#     booktabs = TRUE
#   ) %>%
#   kable_styling(
#     latex_options = c("striped", "hold_position", "scale_down"),
#     full_width    = FALSE
#   )
# 
# # ---- By facility_id ----
# feasibility %>%
#   filter(grepl("12 month", visit_type)) %>%
#   tbl_summary(
#     by        = facility_id,
#     include   = c(fim_1, fim_2, fim_3, fim_4, fim_total),
#     label     = list(fim_1     ~ "IPMH seems implementable",
#                      fim_2     ~ "IPMH seems possible",
#                      fim_3     ~ "IPMH seems doable",
#                      fim_4     ~ "IPMH seems easy to use",
#                      fim_total ~ "Feasibility total score"),
#     type      = list(fim_1     ~ "continuous",
#                      fim_2     ~ "continuous",
#                      fim_3     ~ "continuous",
#                      fim_4     ~ "continuous",
#                      fim_total ~ "continuous"),
#     statistic = list(all_continuous() ~ "{mean} ({sd})"),
#     missing   = "no"
#   ) %>%
#   add_overall() %>%
#   add_p() %>%
#   bold_labels() %>%
#   as_kable_extra(
#     caption  = "IPMH Feasibility by Facility at 12 months",
#     booktabs = TRUE
#   ) %>%
#   kable_styling(
#     latex_options = c("striped", "hold_position", "scale_down"),
#     full_width    = FALSE
#   )

```

\newpage  

## Stigma scale

A higher score indicates a more stigmatizing attitude. This is measured at baseline, 6 months, and 12 months in both arms. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
stigma_scale <- is_survey_df %>% 
    select(visit_type, arm, pt_id, pt_type, facility_id, 
           starts_with("social_distance_"), diagnostic,
           starts_with("disclose_"), starts_with("recovery_"), 
           starts_with("responsibility_"), danger) %>% 
    filter(!is.na(pt_type)) %>%  # Remove rows where pt_type is NA
    mutate(pt_type = droplevels(factor(pt_type))) %>%
    filter(!is.na(facility_id)) %>%
    mutate(facility_id = droplevels(factor(facility_id))) 
    
#Items 3, 8, 9, 10, 11, 15, 19 required reverse scoring.
#social_distance_2, recovery_1, recovery_2, disclose_5, responsibility_1, danger, social_distance_5

stigma_scale <- stigma_scale %>%
    mutate(across(c(starts_with("social_distance_"), starts_with("recovery_"), 
                    starts_with("disclose_"), starts_with("responsibility_"), danger),
                  ~ case_when(
                      str_detect(., "Completely disagree") ~ 1,
                      str_detect(., "Disagree") ~ 2,
                      str_detect(., "Neither agree nor disagree") ~ 3,
                      str_detect(., "Agree") ~ 4,
                      str_detect(., "Completely agree") ~ 5,
                      TRUE ~ as.numeric(as.character(.))
                  )),
           social_distance_2 = 6 - social_distance_2,
           recovery_1 = 6 - recovery_1,
           recovery_2 = 6 - recovery_2,
           disclose_5 = 6 - disclose_5,
           responsibility_1 = 6 - responsibility_1,
           danger = 6 - danger,
           social_distance_5 = 6 - social_distance_5) %>%
    mutate(
        social_distance = rowSums(select(., starts_with("social_distance_")), na.rm = TRUE),
        recovery = rowSums(select(., starts_with("recovery_")), na.rm = TRUE),
        disclose = rowSums(select(., starts_with("disclose_")), na.rm = TRUE),
        responsbility = rowSums(select(., starts_with("responsibility_")), na.rm = TRUE),
        danger = rowSums(select(., starts_with("danger")), na.rm = TRUE),
        total = rowSums(select(., starts_with("social_distance_"), starts_with("recovery_"), 
                             starts_with("disclose_"), starts_with("responsibility_"), starts_with("danger")), na.rm = TRUE)
    )

#by visit_type
stigma_scale %>% 
  tbl_summary(
    by        = visit_type,
    include   = c(social_distance, recovery, disclose, responsbility, danger, total),
    type      = list(social_distance ~ "continuous",
                     recovery        ~ "continuous",
                     disclose        ~ "continuous",
                     responsbility   ~ "continuous",
                     danger          ~ "continuous",
                     total           ~ "continuous"),
    label     = list(social_distance ~ "Social distance",
                     recovery        ~ "Recovery",
                     disclose        ~ "Disclosure",
                     responsbility   ~ "Responsibility",
                     danger          ~ "Danger",
                     total           ~ "Total score"),
    missing   = "no",
    statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>% 
  add_overall() %>% 
  add_p() %>% 
  bold_labels() %>%
  as_kable_extra(
    caption  = "Stigma Scale Summary by Visit Type",
    booktabs = TRUE
  ) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"),
    full_width    = FALSE
  )

#by arm (range of the scale: 20 - 100)
stigma_scale %>% 
  tbl_summary(
    by        = arm,
    include   = c(social_distance, recovery, disclose, responsbility, danger, total),
    type      = list(social_distance ~ "continuous",
                     recovery        ~ "continuous",
                     disclose        ~ "continuous",
                     responsbility   ~ "continuous",
                     danger          ~ "continuous",
                     total           ~ "continuous"),
    label     = list(social_distance ~ "Social distance",
                     recovery        ~ "Recovery",
                     disclose        ~ "Disclosure",
                     responsbility   ~ "Responsibility",
                     danger          ~ "Danger",
                     total           ~ "Total score"),
    missing   = "no",
    statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>% 
  add_overall() %>% 
  add_p() %>% 
  bold_labels() %>%
  as_kable_extra(
    caption  = "Stigma Scale Summary by Arm",
    booktabs = TRUE
  ) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"),
    full_width    = FALSE
  )

# ---- Friedman test by arm ----
run_friedman <- function(df, arm_name, outcome_var) {
  ids_all_three <- df %>%
    filter(arm == arm_name) %>%
    group_by(pt_id) %>%
    summarise(
      has_baseline = any(grepl("Baseline", visit_type, ignore.case = TRUE)),
      has_6m       = any(grepl("6 month", visit_type)),
      has_12m      = any(grepl("12 month", visit_type))
    ) %>%
    filter(has_baseline & has_6m & has_12m) %>%
    pull(pt_id)
  
  ids_complete <- df %>%
    filter(arm == arm_name, pt_id %in% ids_all_three) %>%
    group_by(pt_id) %>%
    summarise(any_na = any(is.na(.data[[outcome_var]])), .groups = "drop") %>%
    filter(!any_na) %>%
    pull(pt_id)
  
  df %>%
    filter(arm == arm_name, pt_id %in% ids_complete) %>%
    mutate(visit_type = factor(visit_type,
                               levels = c("Baseline", "6 month", "12 month"))) %>%
    friedman_test(as.formula(paste(outcome_var, "~ visit_type | pt_id"))) %>%
    mutate(
      arm       = arm_name,
      p         = round(p, 3),
      statistic = round(statistic, 3)
    )
}

# Run for both arms
friedman_int <- run_friedman(stigma_scale, "Intervention", "total")
friedman_con <- run_friedman(stigma_scale, "Control", "total")

# Combine and display
bind_rows(friedman_int, friedman_con) %>%
  rename(
    `Arm`       = arm,
    `Outcome`   = .y.,
    `N`         = n,
    `Statistic` = statistic,
    `df`        = df,
    `P-value`   = p,
    `Method`    = method
  ) %>%
  select(`Arm`, `Outcome`, `N`, `Statistic`, `df`, `P-value`, `Method`) %>%
  kable(
    caption  = "Friedman Test: Stigma Scale Across Timepoints by Arm",
    booktabs = TRUE,
    align    = "llccccc"
  ) %>%
  kable_styling(
    latex_options = c("striped", "hold_position"),
    full_width    = FALSE
 )

# ---- By pt_type at 12 months ----
# stigma_scale %>%
#   filter(grepl("12 month", visit_type)) %>%
#   tbl_summary(
#     by        = pt_type,
#     include   = c(social_distance, recovery, disclose, responsbility, danger, total),
#     type      = list(social_distance ~ "continuous",
#                      recovery        ~ "continuous",
#                      disclose        ~ "continuous",
#                      responsbility   ~ "continuous",
#                      danger          ~ "continuous",
#                      total           ~ "continuous"),
#     label     = list(social_distance ~ "Social distance",
#                      recovery        ~ "Recovery",
#                      disclose        ~ "Disclosure",
#                      responsbility   ~ "Responsibility",
#                      danger          ~ "Danger",
#                      total           ~ "Total score"),
#     missing   = "no",
#     statistic = list(all_continuous() ~ "{mean} ({sd})")
#   ) %>%
#   add_overall() %>%
#   add_p() %>%
#   bold_labels() %>%
#   as_kable_extra(
#     caption  = "Stigma Scale by Participant Type at 12 months",
#     booktabs = TRUE
#   ) %>%
#   kable_styling(
#     latex_options = c("striped", "hold_position", "scale_down"),
#     full_width    = FALSE
#   )

# ---- By facility_id at 12 months ----
# stigma_scale %>%
#   filter(grepl("12 month", visit_type)) %>%
#   tbl_summary(
#     by        = facility_id,
#     include   = c(social_distance, recovery, disclose, responsbility, danger, total),
#     type      = list(social_distance ~ "continuous",
#                      recovery        ~ "continuous",
#                      disclose        ~ "continuous",
#                      responsbility   ~ "continuous",
#                      danger          ~ "continuous",
#                      total           ~ "continuous"),
#     label     = list(social_distance ~ "Social distance",
#                      recovery        ~ "Recovery",
#                      disclose        ~ "Disclosure",
#                      responsbility   ~ "Responsibility",
#                      danger          ~ "Danger",
#                      total           ~ "Total score"),
#     missing   = "no",
#     statistic = list(all_continuous() ~ "{mean} ({sd})")
#   ) %>%
#   add_overall() %>%
#   add_p() %>%
#   bold_labels() %>%
#   as_kable_extra(
#     caption  = "Stigma Scale by Facility at 12 months",
#     booktabs = TRUE
#   ) %>%
#   kable_styling(
#     latex_options = c("striped", "hold_position", "scale_down"),
#     full_width    = FALSE
#   )
```

\newpage

## Sustainability - Short Program Sustainability Assessment Tool

A higher score indicates a more positive perception of the intervention's sustainability. This is measured at 6 months and 12 months in the intervention arm among facility-in-charges only.

```{r psta, echo=FALSE, message=FALSE, warning=FALSE}
psta_df <- is_survey_df %>% 
    select(visit_type, pt_id, facility_id, pt_type, arm, starts_with("sus_"), 
           sustainability_psat_complete) %>% 
    filter(arm == "Intervention") %>% 
    filter(pt_type == "Facility-in-charge: 23") %>% 
    filter(visit_type %in% c("6 month", "12 month")) %>% 
    filter(!is.na(pt_type)) %>%  # Remove rows where pt_type is NA
    mutate(pt_type = droplevels(factor(pt_type))) %>%
    filter(!is.na(facility_id)) %>%
    mutate(facility_id = droplevels(factor(facility_id))) %>% 
    filter(!is.na(visit_type)) %>%
    mutate(visit_type = droplevels(factor(visit_type)))

#recode
psta_df <- psta_df %>% 
    mutate(across(c(starts_with("sus_")), ~ case_when(
        . == "1 (To little or no extent)" ~ 1,
        . == "2" ~ 2,
        . == "3" ~ 3,
        . == "4" ~ 4,
        . == "5" ~ 5,
        . == "6" ~ 6,
        . == "7 (To a very great extent)" ~ 7,
        . == "Not able to answer" ~ NA_real_,  # Convert to NA
        TRUE ~ as.numeric(as.character(.))  # Ensure numeric conversion
    ))) 

psta_df <- psta_df %>%
    mutate(
        sus_env_total = rowMeans(select(., starts_with("sus_env_")), na.rm = TRUE),
        sus_funding_total = rowMeans(select(., starts_with("sus_funding_")), na.rm = TRUE),
        sus_partner_total = rowMeans(select(., starts_with("sus_partner_")), na.rm = TRUE),
        sus_or_total = rowMeans(select(., starts_with("sus_or_")), na.rm = TRUE),
        sus_eval_total = rowMeans(select(., starts_with("sus_eval_")), na.rm = TRUE),
        sus_adp_total = rowMeans(select(., starts_with("sus_adp_")), na.rm = TRUE),
        sus_com_total = rowMeans(select(., starts_with("sus_com_")), na.rm = TRUE),
        sus_plan_total = rowMeans(select(., starts_with("sus_plan_")), na.rm = TRUE)) %>% 
    mutate(
        sus_total = rowMeans(select(., sus_env_total, sus_funding_total, sus_partner_total, 
                         sus_or_total, sus_eval_total, sus_adp_total, 
                         sus_com_total, sus_plan_total), na.rm = TRUE)
    )

# ---- 1) Sustainability table ----
psta_df %>% 
  tbl_summary(
    by        = visit_type,
    include   = c(sus_env_total, sus_funding_total, sus_partner_total, 
                  sus_or_total, sus_eval_total, sus_adp_total, 
                  sus_com_total, sus_plan_total, sus_total),
    label     = list(sus_env_total     ~ "Environmental support",
                     sus_funding_total ~ "Funding stability",
                     sus_partner_total ~ "Partnerships",
                     sus_or_total      ~ "Organizational capacity",
                     sus_eval_total    ~ "Program Evaluation",
                     sus_adp_total     ~ "Program Adaptation",
                     sus_com_total     ~ "Communications",
                     sus_plan_total    ~ "Strategic Planning",
                     sus_total         ~ "Total score"),
    missing   = "no",
    type      = list(sus_env_total     ~ "continuous",
                     sus_funding_total ~ "continuous",
                     sus_partner_total ~ "continuous",
                     sus_or_total      ~ "continuous",
                     sus_eval_total    ~ "continuous",
                     sus_adp_total     ~ "continuous",
                     sus_com_total     ~ "continuous",
                     sus_plan_total    ~ "continuous",
                     sus_total         ~ "continuous"),
    statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  add_overall() %>%
  add_p() %>%
  bold_labels() %>%
  as_kable_extra(
    caption  = "Sustainability Scale Summary by Visit Type",
    booktabs = TRUE
  ) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"),
    full_width    = FALSE
  )

# ---- Paired Wilcoxon test: 6 month vs 12 month ----
ids_both_sus <- intersect(
  psta_df %>% filter(visit_type == "6 month") %>% pull(pt_id),
  psta_df %>% filter(visit_type == "12 month") %>% pull(pt_id)
)

wide_sus <- psta_df %>%
  filter(pt_id %in% ids_both_sus) %>%
  select(pt_id, visit_type, sus_total) %>%
  pivot_wider(names_from  = visit_type,
              values_from = sus_total) %>%
  rename(sus_6m  = `6 month`,
         sus_12m = `12 month`)

wilcox.test(wide_sus$sus_6m, wide_sus$sus_12m, paired = TRUE) %>%
  tidy() %>%
  mutate(
    statistic = round(statistic, 3),
    p.value   = round(p.value, 3)
  ) %>%
  rename(
    `Statistic` = statistic,
    `P-value`   = p.value,
    `Method`    = method,
    `Alternative` = alternative
  ) %>%
  kable(
    caption  = "Paired Wilcoxon Test: Sustainability Scale (6 month vs 12 month)",
    booktabs = TRUE
  ) %>%
  kable_styling(
    latex_options = c("striped", "hold_position"),
    full_width    = FALSE
  )
```

\newpage

## Sustainability - Normalization Measure Development Questionnaire

A higher score for the first 3 items indicates a more positive perception of the intervention's normalization.
A lower score for the rest of the items indicates a more positive perception of the intervention's normalization.

This is measured at 6 months and 12 months in the intervention arm among all providers in the intervention arm.

```{r nmdq, echo=FALSE, message=FALSE, warning=FALSE}
nmdq_df <- is_survey_df %>% 
    select(visit_type, pt_id, facility_id, pt_type, arm, starts_with("sus2_"), 
           sustainability_nom_complete) %>% 
    filter(arm == "Intervention") %>% 
    filter(visit_type %in% c("6 month", "12 month")) %>% 
    filter(!is.na(pt_type)) %>%  # Remove rows where pt_type is NA
    mutate(pt_type = droplevels(factor(pt_type))) %>%
    filter(!is.na(facility_id)) %>%
    mutate(facility_id = droplevels(factor(facility_id))) %>% 
    filter(!is.na(visit_type)) %>%
    mutate(visit_type = droplevels(factor(visit_type)))

#recode
nmdq_df <- nmdq_df %>% 
    mutate(across(c(starts_with("sus2_familiar")), ~ case_when(
        . == "0: Feels very new" ~ 0,
        . == "1" ~ 1,
        . == "2" ~ 2,
        . == "3" ~ 3,
        . == "4" ~ 4,
        . == "5" ~ 5,
        . == "6" ~ 6,
        . == "7" ~ 7,
        . == "8" ~ 8,
        . == "9" ~ 9,
        . == "10: Feels completely familiar" ~ 10,
        TRUE ~ as.numeric(as.character(.))  # Ensure numeric conversion
    ))) %>% 
    mutate(across(c(starts_with("sus2_normal_")), ~ case_when(
        . == "0: Not at all" ~ 0,
        . == "1" ~ 1,
        . == "2" ~ 2,
        . == "3" ~ 3,
        . == "4" ~ 4,
        . == "5: Somewhat" ~ 5,
        . == "6" ~ 6,
        . == "7" ~ 7,
        . == "8" ~ 8,
        . == "9" ~ 9,
        . == "10: Completely" ~ 10,
        TRUE ~ as.numeric(as.character(.))  # Ensure numeric conversion
    ))) %>% 
    mutate(across(matches("^sus2_[1-4]"), ~ case_when(
        . == "1: Strongly Agree" ~ 1,
        . == "2: Agree" ~ 2,
        . == "3: Neither agree nor disagree" ~ 3,
        . == "4: Disagree" ~ 4,
        . == "5: Strongly disagree" ~ 5,
        . == "6: Not relevant to my role" ~ 6,
        . == "7: Not relevant at this stage" ~ 7,
        . == "8: Not relevant to the intervention" ~ 8,    
        TRUE ~ as.numeric(as.character(.))  # Ensure numeric conversion
    )))

nmdq_df <- nmdq_df %>%
  mutate(
    sus2_familiar_total = rowMeans(select(., starts_with("sus2_familiar")), na.rm = TRUE),
    sus2_normal_now_total = rowMeans(select(., starts_with("sus2_normal_now")), na.rm = TRUE),
    sus2_normal_future_total = rowMeans(select(., starts_with("sus2_normal_will")), na.rm = TRUE),
    sus2_3_2 = ifelse(sus2_3_2 < 6, 6 - sus2_3_2, NA),
    sus2_coherence_total = rowMeans(select(., starts_with("sus2_1")) %>%
                                      mutate(across(everything(), ~ ifelse(. < 6, ., NA))), na.rm = TRUE),
    sus2_cognitive_participation_total = rowMeans(select(., starts_with("sus2_2")) %>%
                                                    mutate(across(everything(), ~ ifelse(. < 6, ., NA))), na.rm = TRUE),
    sus2_collective_action_total = rowMeans(select(., starts_with("sus2_3")) %>%
                                              mutate(across(everything(), ~ ifelse(. < 6, ., NA))), na.rm = TRUE),
    sus2_reflexive_monitoring_total = rowMeans(select(., starts_with("sus2_4")) %>%
                                                 mutate(across(everything(), ~ ifelse(. < 6, ., NA))), na.rm = TRUE)
  ) %>%
  mutate(
    sus2_total = rowMeans(select(., sus2_coherence_total, sus2_cognitive_participation_total,
                                 sus2_collective_action_total, sus2_reflexive_monitoring_total), na.rm = TRUE)
  )

# ---- By visit_type ----
nmdq_df %>% 
  tbl_summary(
    by        = visit_type,
    include   = c(sus2_familiar_total, sus2_normal_now_total, 
                  sus2_normal_future_total, sus2_coherence_total, 
                  sus2_cognitive_participation_total, 
                  sus2_collective_action_total, 
                  sus2_reflexive_monitoring_total, 
                  sus2_total),
    label     = list(sus2_familiar_total                ~ "Familiarity with IPMH",
                     sus2_normal_now_total              ~ "Normalization now",
                     sus2_normal_future_total           ~ "Normalization in future",
                     sus2_coherence_total               ~ "Coherence",
                     sus2_cognitive_participation_total ~ "Cognitive participation",
                     sus2_collective_action_total       ~ "Collective action",
                     sus2_reflexive_monitoring_total    ~ "Reflexive monitoring",
                     sus2_total                         ~ "Total score"),
    missing   = "no",
    type      = list(sus2_familiar_total                ~ "continuous",
                     sus2_normal_now_total              ~ "continuous",
                     sus2_normal_future_total           ~ "continuous",
                     sus2_coherence_total               ~ "continuous",
                     sus2_cognitive_participation_total ~ "continuous",
                     sus2_collective_action_total       ~ "continuous",
                     sus2_reflexive_monitoring_total    ~ "continuous",
                     sus2_total                         ~ "continuous"),
    statistic = list(all_continuous() ~ "{mean} ({sd})")
  ) %>%
  add_overall() %>%
  add_p() %>%
  bold_labels() %>%
  as_kable_extra(
    caption  = "NMDQ by Visit Type",
    booktabs = TRUE
  ) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"),
    full_width    = FALSE
  )

# ---- Paired Wilcoxon test ----
ids_both_nmdq <- intersect(
  nmdq_df %>% filter(grepl("6 month", visit_type)) %>% pull(pt_id),
  nmdq_df %>% filter(grepl("12 month", visit_type)) %>% pull(pt_id)
)

wide_nmdq <- nmdq_df %>%
  filter(pt_id %in% ids_both_nmdq) %>%
  select(pt_id, visit_type, 
         sus2_familiar_total, sus2_normal_now_total,
         sus2_normal_future_total, sus2_coherence_total,
         sus2_cognitive_participation_total,
         sus2_collective_action_total,
         sus2_reflexive_monitoring_total,
         sus2_total) %>%
  pivot_wider(names_from  = visit_type,
              values_from = c(sus2_familiar_total, sus2_normal_now_total,
                              sus2_normal_future_total, sus2_coherence_total,
                              sus2_cognitive_participation_total,
                              sus2_collective_action_total,
                              sus2_reflexive_monitoring_total,
                              sus2_total))

outcomes <- c("sus2_familiar_total", "sus2_normal_now_total",
              "sus2_normal_future_total", "sus2_coherence_total",
              "sus2_cognitive_participation_total",
              "sus2_collective_action_total",
              "sus2_reflexive_monitoring_total",
              "sus2_total")

outcome_labels <- c("Familiarity with IPMH", "Normalization now",
                    "Normalization in future", "Coherence",
                    "Cognitive participation", "Collective action",
                    "Reflexive monitoring", "Total score")

paired_nmdq <- map2_dfr(outcomes, outcome_labels, function(var, label) {
  v6m  <- wide_nmdq[[paste0(var, "_6 month")]]
  v12m <- wide_nmdq[[paste0(var, "_12 month")]]
  
  wt <- wilcox.test(v6m, v12m, paired = TRUE, conf.int = TRUE)
  
  tibble(
    Outcome         = label,
    `Median (6mo)`  = round(median(v6m,  na.rm = TRUE), 2),
    `Median (12mo)` = round(median(v12m, na.rm = TRUE), 2),
    `Median Diff`   = round(median(v12m - v6m, na.rm = TRUE), 2),
    `95% CI`        = sprintf("(%.2f, %.2f)", wt$conf.int[1], wt$conf.int[2]),
    `W-statistic`   = round(wt$statistic, 3),
    `P-value`       = round(wt$p.value, 3)
  )
})

paired_nmdq %>%
  kable(
    caption  = "Paired Wilcoxon Test: NMDQ (6 month vs 12 month)",
    booktabs = TRUE,
    align    = "lcccccc"
  ) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"),
    full_width    = FALSE
  )

# # ---- By pt_type at 12 months ----
# nmdq_df %>%
#   filter(grepl("12 month", visit_type)) %>%
#   tbl_summary(
#     by        = pt_type,
#     include   = c(sus2_familiar_total, sus2_normal_now_total,
#                   sus2_normal_future_total, sus2_coherence_total,
#                   sus2_cognitive_participation_total,
#                   sus2_collective_action_total,
#                   sus2_reflexive_monitoring_total,
#                   sus2_total),
#     label     = list(sus2_familiar_total                ~ "Familiarity with IPMH",
#                      sus2_normal_now_total              ~ "Normalization now",
#                      sus2_normal_future_total           ~ "Normalization in future",
#                      sus2_coherence_total               ~ "Coherence",
#                      sus2_cognitive_participation_total ~ "Cognitive participation",
#                      sus2_collective_action_total       ~ "Collective action",
#                      sus2_reflexive_monitoring_total    ~ "Reflexive monitoring",
#                      sus2_total                         ~ "Total score"),
#     missing   = "no",
#     type      = list(sus2_familiar_total                ~ "continuous",
#                      sus2_normal_now_total              ~ "continuous",
#                      sus2_normal_future_total           ~ "continuous",
#                      sus2_coherence_total               ~ "continuous",
#                      sus2_cognitive_participation_total ~ "continuous",
#                      sus2_collective_action_total       ~ "continuous",
#                      sus2_reflexive_monitoring_total    ~ "continuous",
#                      sus2_total                         ~ "continuous"),
#     statistic = list(all_continuous() ~ "{mean} ({sd})")
#   ) %>%
#   add_overall() %>%
#   add_p() %>%
#   bold_labels() %>%
#   as_kable_extra(
#     caption  = "NMDQ by Participant Type at 12 months",
#     booktabs = TRUE
#   ) %>%
#   kable_styling(
#     latex_options = c("striped", "hold_position", "scale_down"),
#     full_width    = FALSE
#   )
# 
# # ---- By facility_id at 12 months ----
# nmdq_df %>%
#   filter(grepl("12 month", visit_type)) %>%
#   tbl_summary(
#     by        = facility_id,
#     include   = c(sus2_familiar_total, sus2_normal_now_total,
#                   sus2_normal_future_total, sus2_coherence_total,
#                   sus2_cognitive_participation_total,
#                   sus2_collective_action_total,
#                   sus2_reflexive_monitoring_total,
#                   sus2_total),
#     label     = list(sus2_familiar_total                ~ "Familiarity with IPMH",
#                      sus2_normal_now_total              ~ "Normalization now",
#                      sus2_normal_future_total           ~ "Normalization in future",
#                      sus2_coherence_total               ~ "Coherence",
#                      sus2_cognitive_participation_total ~ "Cognitive participation",
#                      sus2_collective_action_total       ~ "Collective action",
#                      sus2_reflexive_monitoring_total    ~ "Reflexive monitoring",
#                      sus2_total                         ~ "Total score"),
#     missing   = "no",
#     type      = list(sus2_familiar_total                ~ "continuous",
#                      sus2_normal_now_total              ~ "continuous",
#                      sus2_normal_future_total           ~ "continuous",
#                      sus2_coherence_total               ~ "continuous",
#                      sus2_cognitive_participation_total ~ "continuous",
#                      sus2_collective_action_total       ~ "continuous",
#                      sus2_reflexive_monitoring_total    ~ "continuous",
#                      sus2_total                         ~ "continuous"),
#     statistic = list(all_continuous() ~ "{mean} ({sd})")
#   ) %>%
#   add_overall() %>%
#   add_p() %>%
#   bold_labels() %>%
#   as_kable_extra(
#     caption  = "NMDQ by Facility at 12 months",
#     booktabs = TRUE
#   ) %>%
#   kable_styling(
#     latex_options = c("striped", "hold_position", "scale_down"),
#     full_width    = FALSE
#   )
```

